### 2017-04-22 paper.tex
Started on rough rough draft

\documentclass{article}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{color}

\begin{document}
\section*{Modified Teaching environment}
We will solve a more relaxed problem such that the teacher may not only give $(x,y)$ training examples but may also give single $x$ values to probe the learner for output.

\section*{Theorem 1}
If given a perceptron with known starting parameter $w_0$, desired parameter $w^*$, and unknown learning rate $\eta \in [\alpha , \beta]$ for given $\epsilon > 0$, we can guarantee $\eta \in [\alpha', \beta']$ such that $\beta' - \alpha' \leq \epsilon$ using $1 + \lceil \log_2(\frac{\beta - \alpha}{\epsilon})\rceil$

\subsection*{Proof:}
Assume $w_0 \neq cw^*$ for arbitrary $c > 0$, then there exists an $(x_1, y_1)$ such that $\text{sign}(\langle w^*,x_1 \rangle) = y_1 = 1$ and $\text{sign}(\langle w_0,x_1 \rangle) = -y_1$.
\color{red}
I don't think that its hard to show this is true.
\color{black}

Then give $(x_1, y_1)$ to the learner and then after training update,
$$
w_1 = w_0 + \eta* x_1
$$

Then grab an unlabeled $x_2$ such that
$\langle w_0,x_2 \rangle \neq 0$, $\langle x_1, x_2 \rangle \neq 0$
and 
$$
\langle w_0,x_2 \rangle + \frac{\beta - \alpha}{2} \langle x_1, x_2 \rangle = 0
$$
\color{red}
I'm a moron. What's the closed form of this? I know there is not a unique solution. We just need the simplest one.
\color{black}

Then probe the learner with $x_2$. If the learner outputs $+1$ then
$\eta \in (\frac{\beta - \alpha}{2} , \beta]$, else 
$\eta \in [\alpha,\frac{\beta - \alpha}{2}]$

As you can see our interval for $\eta$ halves with each probe. One can then see that we can iteratively repeat this for a total of $ \lceil \log_2(\frac{\beta - \alpha}{\epsilon})\rceil$ iterations to aquire the desired interval length on $\eta$.

\section*{Theorem 2}
\color{red}

Something to the respect of, if we know $\eta \in [\alpha, \beta]$ then with one training example we can guarantee that
$$
\frac{\langle w^*, w_0 \rangle}{\lvert w^* \rvert \lvert w_0 \rvert} \geq 1 - \epsilon
$$

So by combining with Theorem 1
$$
T_\epsilon \leq \{\text{number of points needed to guarantee } \eta \in [\alpha, \beta]\} +1 
$$
Where $T_\epsilon$ is the $\epsilon$ teaching dimension of the perceptron.
\color{black}

\subsection*{Proof}

\color{red}
Assume we now $w_1$
and $\eta_{min} \leq \eta \leq \eta_{max}$

and there is an $(x_2,y_2)$ such that $y_2 = 1$ and agrees with $w^*$ and not $w_1$. For some $c$ similar to orignal proof
let 
$$
x_2 = \frac{cw^* - w_1}{\beta}
$$

note 
$$
\frac{\alpha}{\alpha + \beta - \alpha}\leq \frac{\eta}{\beta}  \leq 1
$$

so
$$
w_1 + \eta x_2 = cw^* - \epsilon
$$
where
$
0 \leq \epsilon \leq (cw* - w_1) * \frac{\beta - \alpha}{\alpha + \beta - \alpha}  \leq \frac{\beta - \alpha}{\eta_{min} + \beta - \alpha} \leq \frac{\beta - \alpha}{\eta_{min}}
$

\color{red}

\end{document}

### 2017-04-23 paper.tex
Got half way through basic bound proof

@@
 \usepackage{color}
+\usepackage{parskip}
+
+\setlength{\parskip}{5pt}
+\setlength{\parindent}{0pt}
 
@@
 \section*{Theorem 1}
-If given a perceptron with known starting parameter $w_0$, desired parameter $w^*$, and unknown learning rate $\eta \in [\alpha , \beta]$ for given $\epsilon > 0$, we can guarantee $\eta \in [\alpha', \beta']$ such that $\beta' - \alpha' \leq \epsilon$ using $1 + \lceil \log_2(\frac{\beta - \alpha}{\epsilon})\rceil$
+If given a perceptron with known starting parameter $w_0$, desired parameter $w^*$, and unknown learning rate $\eta \in [\alpha , \beta]$ for given $\epsilon > 0$, we can guarantee $\eta \in [\alpha', \beta']$ such that $\beta' - \alpha' \leq \epsilon$ using $1 + \lceil \log_2(\frac{\beta - \alpha}{\epsilon})\rceil$ examples.=
 
@@
 
-\color{red}
-Assume we now $w_1$
-and $\eta_{min} \leq \eta \leq \eta_{max}$
+Assume $w_0$ is known and $\eta \in [\eta_{\min} , \eta_{\max}] $ such that 
+$0 < \eta_{\min} < \eta_{\max} < \infty$
 
-and there is an $(x_2,y_2)$ such that $y_2 = 1$ and agrees with $w^*$ and not $w_1$. For some $c$ similar to orignal proof
-let 
-$$
-x_2 = \frac{cw^* - w_1}{\beta}
-$$
+Assume WLOG $\lVert w^* \rVert = 1$.
 
-note 
-$$
-\frac{\alpha}{\alpha + \beta - \alpha}\leq \frac{\eta}{\beta}  \leq 1
-$$
-
-so
-$$
-w_1 + \eta x_2 = cw^* - \epsilon
-$$
-where
-$
-0 \leq \epsilon \leq (cw* - w_1) * \frac{\beta - \alpha}{\alpha + \beta - \alpha}  \leq \frac{\beta - \alpha}{\eta_{min} + \beta - \alpha} \leq \frac{\beta - \alpha}{\eta_{min}}
-$
+Pick $(x_1,y_1)$ such that $y_1 = -1$, $\lVert x_1 \rVert = \frac{2 \lVert w_0 \rVert}{\epsilon \eta_{\min}}$
 
 \color{red}
+Note when i say $y_1 = 1$, that implies that it agrees with $w^*$. And I'm pretty 
+sure the above statement is valid. I think such an $x,y$ pair will always exist if
+$w_0$ disagrees with $w^*$.
+\color{black}
+
+Then use the method from Theorem 1 to get a bound on $\eta$ such that $\eta \in [\alpha , \beta]$ and $\beta - \alpha <= ?$
+
+Then let $x_2 = \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2}w^* + x_1$.
+It should be clear that then $y_2 = 1$
+
+Then realize that
+$w_1 = w_0 - \eta x_1$
+
+So
+$$
+y_2 \langle w_1, x_2 \rangle  = \bigg\langle \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0 - \eta x_1 \bigg\rangle
+$$
+$$
+= \bigg\langle \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0  \bigg\rangle - \eta \lVert x_1 \rVert^2
+$$
+$$
+\leq \bigg( \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} \lVert w^* \rVert + \lVert x_1 \rVert \bigg ) \lVert w_0 \rVert - \eta \lVert x_1 \rVert^2
+$$
+$$
+= \frac{4 \lVert w_0 \rVert^2}{\epsilon (\beta + \alpha)/2} - \eta \frac{4 \lVert w_0 \rVert^2}{\epsilon^2 \eta_{\min}^2}
+$$
+$$
+\leq \frac{4 \lVert w_0 \rVert^2}{\epsilon (\beta + \alpha)/2} -  \frac{4 \lVert w_0 \rVert^2}{\epsilon^2 \eta_{\min}}
+$$
+which is less than $0$ for $epsilon < 1$
 

### 2017-04-27 paper_final.tex
Started on final NIPs style paper

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

%\usepackage{nips_2016}

% to compile a camera-ready version, add the [final] option, e.g.:
 \usepackage[final]{nips_2016}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\title{An Extension of Optimal Teaching For Online Perceptrons}

\author{
  Max Horowitz-Gelb \qquad Gabriel Ferns\\
  Department of Computer Sciences, University of Wisconsin-Madison\\
  \texttt{\{horowitzgelb, ferns\}@wisc.edu}\\
}

\begin{document}
% \nipsfinalcopy is no longer used

\maketitle

\begin{abstract}
  Optimal teaching is the task of constructing a special efficient training set, which when given to a learner teaches the desired concept inside the learners concept class. Before \cite{perceptron}, analysis of optimal teaching was only focused on batch learners. \cite{perceptron} looked at the optimal teaching strategy of a Perceptron in two different scenarios with varying degrees of knowledge of the initial state of the learner. In this paper we show extensions of these scenarios where knowledge of the initial state is even more unknown.
\end{abstract}

\section{Introduction}

\section{Teaching Dimension}

\subsection{Style}

Papers to be submitted to NIPS 2016 must be prepared according to the
instructions presented here. Papers may only be up to eight pages
long, including figures. Since 2009 an additional ninth page
\emph{containing only acknowledgments and/or cited references} is
allowed. Papers that exceed nine pages will not be reviewed, or in any
other way considered for presentation at the conference.

The margins in 2016 are the same as since 2007, which allow for
$\sim15\%$ more words in the paper compared to earlier years.

Authors are required to use the NIPS \LaTeX{} style files obtainable
at the NIPS website as indicated below. Please make sure you use the
current files and not previous versions. Tweaking the style files may
be grounds for rejection.

\subsection{Retrieval of style files}

The style files for NIPS and other conference information are
available on the World Wide Web at
\begin{center}
  \url{http://www.nips.cc/}
\end{center}
The file \verb+nips_2016.pdf+ contains these instructions and
illustrates the various formatting requirements your NIPS paper must
satisfy.

The only supported style file for NIPS 2016 is \verb+nips_2016.sty+,
rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{}
  2.09, Microsoft Word, and RTF are no longer supported!}

The new \LaTeX{} style file contains two optional arguments:
\verb+final+, which creates a camera-ready copy, and \verb+nonatbib+,
which will not load the \verb+natbib+ package for you in case of
package clash.

At submission time, please omit the \verb+final+ option. This will
anonymize your submission and add line numbers to aid review.  Please
do \emph{not} refer to these line numbers in your paper as they will
be removed during generation of camera-ready copies.

The file \verb+nips_2016.tex+ may be used as a ``shell'' for writing
your paper. All you have to do is replace the author, title, abstract,
and text of the paper with your own.

The formatting instructions contained in these style files are
summarized in Sections \ref{gen_inst}, \ref{headings}, and
\ref{others} below.

\section{General formatting instructions}
\label{gen_inst}

The text must be confined within a rectangle 5.5~inches (33~picas)
wide and 9~inches (54~picas) long. The left margin is 1.5~inch
(9~picas).  Use 10~point type with a vertical spacing (leading) of
11~points.  Times New Roman is the preferred typeface throughout, and
will be selected for you by default.  Paragraphs are separated by
\nicefrac{1}{2}~line space (5.5 points), with no indentation.

The paper title should be 17~point, initial caps/lower case, bold,
centered between two horizontal rules. The top rule should be 4~points
thick and the bottom rule should be 1~point thick. Allow
\nicefrac{1}{4}~inch space above and below the title to rules. All
pages should start at 1~inch (6~picas) from the top of the page.

For the final version, authors' names are set in boldface, and each
name is centered above the corresponding address. The lead author's
name is to be listed first (left-most), and the co-authors' names (if
different address) are set to follow. If there is only one co-author,
list both author and co-author side by side.

Please pay special attention to the instructions in Section \ref{others}
regarding figures, tables, acknowledgments, and references.

\section{Headings: first level}
\label{headings}

All headings should be lower case (except for first word and proper
nouns), flush left, and bold.

First-level headings should be in 12-point type.

\subsection{Headings: second level}

Second-level headings should be in 10-point type.

\subsubsection{Headings: third level}

Third-level headings should be in 10-point type.

\paragraph{Paragraphs}

There is also a \verb+\paragraph+ command available, which sets the
heading in bold, flush left, and inline with the text, with the
heading followed by 1\,em of space.

\section{Citations, figures, tables, references}
\label{others}

These instructions apply to everyone.

\subsection{Citations within the text}

The \verb+natbib+ package will be loaded for you by default.
Citations may be author/year or numeric, as long as you maintain
internal consistency.  As to the format of the references themselves,
any style is acceptable as long as it is used consistently.

The documentation for \verb+natbib+ may be found at
\begin{center}
  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
\end{center}
Of note is the command \verb+\citet+, which produces citations
appropriate for use in inline text.  For example,
\begin{verbatim}
   \citet{hasselmo} investigated\dots
\end{verbatim}
produces
\begin{quote}
  Hasselmo, et al.\ (1995) investigated\dots
\end{quote}

If you wish to load the \verb+natbib+ package with options, you may
add the following before loading the \verb+nips_2016+ package:
\begin{verbatim}
   \PassOptionsToPackage{options}{natbib}
\end{verbatim}

If \verb+natbib+ clashes with another package you load, you can add
the optional argument \verb+nonatbib+ when loading the style file:
\begin{verbatim}
   \usepackage[nonatbib]{nips_2016}
\end{verbatim}

As submission is double blind, refer to your own published work in the
third person. That is, use ``In the previous work of Jones et
al.\ [4],'' not ``In our previous work [4].'' If you cite your other
papers that are not widely available (e.g., a journal paper under
review), use anonymous author names in the citation, e.g., an author
of the form ``A.\ Anonymous.''

\subsection{Footnotes}

Footnotes should be used sparingly.  If you do require a footnote,
indicate footnotes with a number\footnote{Sample of the first
  footnote.} in the text. Place the footnotes at the bottom of the
page on which they appear.  Precede the footnote with a horizontal
rule of 2~inches (12~picas).

Note that footnotes are properly typeset \emph{after} punctuation
marks.\footnote{As in this example.}

\subsection{Figures}

All artwork must be neat, clean, and legible. Lines should be dark
enough for purposes of reproduction. The figure number and caption
always appear after the figure. Place one line space before the figure
caption and one line space after the figure. The figure caption should
be lower case (except for first word and proper nouns); figures are
numbered consecutively.

You may use color figures.  However, it is best for the figure
captions and the paper body to be legible if the paper is printed in
either black/white or in color.
\begin{figure}[h]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  \caption{Sample figure caption.}
\end{figure}

\subsection{Tables}

All tables must be centered, neat, clean and legible.  The table
number and title always appear before the table.  See
Table~\ref{sample-table}.

Place one line space before the table title, one line space after the
table title, and one line space after the table. The table title must
be lower case (except for first word and proper nouns); tables are
numbered consecutively.

Note that publication-quality tables \emph{do not contain vertical
  rules.} We strongly suggest the use of the \verb+booktabs+ package,
which allows for typesetting high-quality, professional tables:
\begin{center}
  \url{https://www.ctan.org/pkg/booktabs}
\end{center}
This package was used to typeset Table~\ref{sample-table}.

\begin{table}[t]
  \caption{Sample table title}
  \label{sample-table}
  \centering
  \begin{tabular}{lll}
    \toprule
    \multicolumn{2}{c}{Part}                   \\
    \cmidrule{1-2}
    Name     & Description     & Size ($\mu$m) \\
    \midrule
    Dendrite & Input terminal  & $\sim$100     \\
    Axon     & Output terminal & $\sim$10      \\
    Soma     & Cell body       & up to $10^6$  \\
    \bottomrule
  \end{tabular}
\end{table}

\section{Final instructions}

Do not change any aspects of the formatting parameters in the style
files.  In particular, do not modify the width or length of the
rectangle the text should fit into, and do not change font sizes
(except perhaps in the \textbf{References} section; see below). Please
note that pages should be numbered.

\section{Preparing PDF files}

Please prepare submission files with paper size ``US Letter,'' and
not, for example, ``A4.''

Fonts were the main cause of problems in the past years. Your PDF file
must only contain Type 1 or Embedded TrueType fonts. Here are a few
instructions to achieve this.

\begin{itemize}

\item You should directly generate PDF files using \verb+pdflatex+.

\item You can check which fonts a PDF files uses.  In Acrobat Reader,
  select the menu Files$>$Document Properties$>$Fonts and select Show
  All Fonts. You can also use the program \verb+pdffonts+ which comes
  with \verb+xpdf+ and is available out-of-the-box on most Linux
  machines.

\item The IEEE has recommendations for generating PDF files whose
  fonts are also acceptable for NIPS. Please see
  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}

\item \verb+xfig+ "patterned" shapes are implemented with bitmap
  fonts.  Use "solid" shapes instead.

\item The \verb+\bbold+ package almost always uses bitmap fonts.  You
  should use the equivalent AMS Fonts:
\begin{verbatim}
   \usepackage{amsfonts}
\end{verbatim}
followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or
\verb+\mathbb{C}+ for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You
can also use the following workaround for reals, natural and complex:
\begin{verbatim}
   \newcommand{\RR}{I\!\!R} %real numbers
   \newcommand{\Nat}{I\!\!N} %natural numbers
   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
\end{verbatim}
Note that \verb+amsfonts+ is automatically loaded by the
\verb+amssymb+ package.

\end{itemize}

If your file contains type 3 fonts or non embedded TrueType fonts, we
will ask you to fix it.

\subsection{Margins in \LaTeX{}}

Most of the margin problems come from figures positioned by hand using
\verb+\special+ or other commands. We suggest using the command
\verb+\includegraphics+ from the \verb+graphicx+ package. Always
specify the figure width as a multiple of the line width as in the
example below:
\begin{verbatim}
   \usepackage[pdftex]{graphicx} ...
   \includegraphics[width=0.8\linewidth]{myfile.pdf}
\end{verbatim}
See Section 4.4 in the graphics bundle documentation
(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})

A number of width problems arise when \LaTeX{} cannot properly
hyphenate a line. Please give LaTeX hyphenation hints using the
\verb+\-+ command when necessary.

\subsubsection*{Acknowledgments}

Use unnumbered third level headings for the acknowledgments. All
acknowledgments go at the end of the paper. Do not include
acknowledgments in the anonymized submission, only in the final paper.

\section*{References}

References follow the acknowledgments. Use unnumbered first-level
heading for the references. Any choice of citation style is acceptable
as long as you are consistent. It is permissible to reduce the font
size to \verb+small+ (9 point) when listing the references. {\bf
  Remember that you can use a ninth page as long as it contains
  \emph{only} cited references.}
\medskip

\small
\bibliography{paper_bib}
\bibliographystyle{plain}

\end{document}

### 2017-04-27 paper_final.tex
more work on intro

@@
 \documentclass{article}
-
-% if you need to pass options to natbib, use, e.g.:
-% \PassOptionsToPackage{numbers, compress}{natbib}
-% before loading nips_2016
-%
-% to avoid loading the natbib package, add option nonatbib:
-% \usepackage[nonatbib]{nips_2016}
-
-%\usepackage{nips_2016}
-
-% to compile a camera-ready version, add the [final] option, e.g.:
- \usepackage[final]{nips_2016}
 
@@
 \usepackage{microtype}      % microtypography
-\title{An Extension of Optimal Teaching For Online Perceptrons}
+\usepackage{algorithm}
+\usepackage{algorithmic}
+\usepackage{bbm}
+\usepackage{parskip}
+
+\setlength{\parskip}{5pt}
+\setlength{\parindent}{0pt}
+
+\title{\rule{350pt}{5pt}\\ \textbf{An Extension of Optimal Teaching For Online Perceptrons} \\ \rule{350pt}{1pt}}
 
 \author{
-  Max Horowitz-Gelb \qquad Gabriel Ferns\\
+  \textbf{Max Horowitz-Gelb \qquad Gabriel Ferns}\\
   Department of Computer Sciences, University of Wisconsin-Madison\\
@@
 Before \cite{perceptron}, analysis of optimal teaching was only focused on batch learners.
-\cite{perceptron} looked at the optimal teaching strategy of a Perceptron in two different scenarios with varying degrees of knowledge of the initial state of the learner.
+\cite{perceptron} looked at the optimal teaching strategy of an online Perceptron in two different scenarios with varying degrees of knowledge of the initial state of the learner.
 In this paper we show extensions of these scenarios where knowledge of the initial state is even more unknown.
@@
 \section{Introduction}
+There may be a scenario where one entity, or the \textit{teacher},  has a desired target concept and a learner in which the teacher wants to embed that concept.
+In this scenario the teacher can only interact with the learner by constructing and then giving the learner a set of training examples.
+This constructive task is known as optimal teaching \cite{machine_teaching} \cite{teaching_dimension}.
+\cite{perceptron} looked for the first time at online teaching in an online environment, with an online perceptron.
+In this paper we look at optimal teaching of the same perceptron, but now we give the teacher the ability to use unlabeled examples.
+Unlabeled examples allow the teacher to probe to discover more about the learners current state while not changing the learner.
+We show that this new added ability allows the teacher to teach an online perceptron in a scenario, that before may have been difficult.
+
+The specific perceptron we are teaching is the  online perceptron \cite{perceptron_algo}. The algorithm is designed for a binary classification. It can learn any linear decision boundary,
+with mapping $x \to sign(\langle w, x \rangle)$ where $x \in \mathbb{R}^d$ comes from the input space and $w \in \mathbb{R}^d$ parameterizes the perceptron.
+Here , as in \cite{perceptron}, $sign(0) = -1$ for completeness.
+The learning algorithm for the online perceptron is seen below.
+
+\begin{algorithm}
+\caption{Online Perceptron}
+\begin{algorithmic}[1]
+	\REQUIRE Initial weight vector $w_0 \in \mathbb{R}^d$, learning rate $\eta > 0$
+	\FOR{$t \in 1$ ...}
+    	\STATE receive $x_t$
+    	\STATE predict $\hat{y}_t = sign(\langle w_{t-1} , x_t \rangle)$
+    	\STATE receive $y_t$
+    	\STATE $w_t \leftarrow w_{t-1} + \mathbbm{1}_{y_t \langle w_{t-1} , x_t \rangle \leq 0} \eta x_t$
+    \ENDFOR
+\end{algorithmic}
+\end{algorithm}
+
+As one can see, knowledge of $w_0$ and $\eta$ are critical to being able to teach an online perceptron learner.
+\cite{perceptron} looked at teaching a perceptron with and without knowledge of $w_0$.
+Here we look at the situation when the learning rate $\eta$ is unknown.
+As well we look at the most challenging case, when both $w_0$ and $\eta$ are unknown at the start of teaching.
 
@@
 
-\subsection{Style}
-
-Papers to be submitted to NIPS 2016 must be prepared according to the
-instructions presented here. Papers may only be up to eight pages
-long, including figures. Since 2009 an additional ninth page
-\emph{containing only acknowledgments and/or cited references} is
-allowed. Papers that exceed nine pages will not be reviewed, or in any
-other way considered for presentation at the conference.
-
-The margins in 2016 are the same as since 2007, which allow for
-$\sim15\%$ more words in the paper compared to earlier years.
-
-Authors are required to use the NIPS \LaTeX{} style files obtainable
-at the NIPS website as indicated below. Please make sure you use the
-current files and not previous versions. Tweaking the style files may
-be grounds for rejection.
-
-\subsection{Retrieval of style files}
-
-The style files for NIPS and other conference information are
-available on the World Wide Web at
-\begin{center}
-  \url{http://www.nips.cc/}
-\end{center}
-The file \verb+nips_2016.pdf+ contains these instructions and
-illustrates the various formatting requirements your NIPS paper must
-satisfy.
-
-The only supported style file for NIPS 2016 is \verb+nips_2016.sty+,
-rewritten for \LaTeXe{}.  \textbf{Previous style files for \LaTeX{}
-  2.09, Microsoft Word, and RTF are no longer supported!}
-
-The new \LaTeX{} style file contains two optional arguments:
-\verb+final+, which creates a camera-ready copy, and \verb+nonatbib+,
-which will not load the \verb+natbib+ package for you in case of
-package clash.
-
-At submission time, please omit the \verb+final+ option. This will
-anonymize your submission and add line numbers to aid review.  Please
-do \emph{not} refer to these line numbers in your paper as they will
-be removed during generation of camera-ready copies.
-
-The file \verb+nips_2016.tex+ may be used as a ``shell'' for writing
-your paper. All you have to do is replace the author, title, abstract,
-and text of the paper with your own.
-
-The formatting instructions contained in these style files are
-summarized in Sections \ref{gen_inst}, \ref{headings}, and
-\ref{others} below.
-
-\section{General formatting instructions}
-\label{gen_inst}
-
-The text must be confined within a rectangle 5.5~inches (33~picas)
-wide and 9~inches (54~picas) long. The left margin is 1.5~inch
-(9~picas).  Use 10~point type with a vertical spacing (leading) of
-11~points.  Times New Roman is the preferred typeface throughout, and
-will be selected for you by default.  Paragraphs are separated by
-\nicefrac{1}{2}~line space (5.5 points), with no indentation.
-
-The paper title should be 17~point, initial caps/lower case, bold,
-centered between two horizontal rules. The top rule should be 4~points
-thick and the bottom rule should be 1~point thick. Allow
-\nicefrac{1}{4}~inch space above and below the title to rules. All
-pages should start at 1~inch (6~picas) from the top of the page.
-
-For the final version, authors' names are set in boldface, and each
-name is centered above the corresponding address. The lead author's
-name is to be listed first (left-most), and the co-authors' names (if
-different address) are set to follow. If there is only one co-author,
-list both author and co-author side by side.
-
-Please pay special attention to the instructions in Section \ref{others}
-regarding figures, tables, acknowledgments, and references.
-
-\section{Headings: first level}
-\label{headings}
-
-All headings should be lower case (except for first word and proper
-nouns), flush left, and bold.
-
-First-level headings should be in 12-point type.
-
-\subsection{Headings: second level}
-
-Second-level headings should be in 10-point type.
-
-\subsubsection{Headings: third level}
-
-Third-level headings should be in 10-point type.
-
-\paragraph{Paragraphs}
-
-There is also a \verb+\paragraph+ command available, which sets the
-heading in bold, flush left, and inline with the text, with the
-heading followed by 1\,em of space.
-
-\section{Citations, figures, tables, references}
-\label{others}
-
-These instructions apply to everyone.
-
-\subsection{Citations within the text}
-
-The \verb+natbib+ package will be loaded for you by default.
-Citations may be author/year or numeric, as long as you maintain
-internal consistency.  As to the format of the references themselves,
-any style is acceptable as long as it is used consistently.
-
-The documentation for \verb+natbib+ may be found at
-\begin{center}
-  \url{http://mirrors.ctan.org/macros/latex/contrib/natbib/natnotes.pdf}
-\end{center}
-Of note is the command \verb+\citet+, which produces citations
-appropriate for use in inline text.  For example,
-\begin{verbatim}
-   \citet{hasselmo} investigated\dots
-\end{verbatim}
-produces
-\begin{quote}
-  Hasselmo, et al.\ (1995) investigated\dots
-\end{quote}
-
-If you wish to load the \verb+natbib+ package with options, you may
-add the following before loading the \verb+nips_2016+ package:
-\begin{verbatim}
-   \PassOptionsToPackage{options}{natbib}
-\end{verbatim}
-
-If \verb+natbib+ clashes with another package you load, you can add
-the optional argument \verb+nonatbib+ when loading the style file:
-\begin{verbatim}
-   \usepackage[nonatbib]{nips_2016}
-\end{verbatim}
-
-As submission is double blind, refer to your own published work in the
-third person. That is, use ``In the previous work of Jones et
-al.\ [4],'' not ``In our previous work [4].'' If you cite your other
-papers that are not widely available (e.g., a journal paper under
-review), use anonymous author names in the citation, e.g., an author
-of the form ``A.\ Anonymous.''
-
-\subsection{Footnotes}
-
-Footnotes should be used sparingly.  If you do require a footnote,
-indicate footnotes with a number\footnote{Sample of the first
-  footnote.} in the text. Place the footnotes at the bottom of the
-page on which they appear.  Precede the footnote with a horizontal
-rule of 2~inches (12~picas).
-
-Note that footnotes are properly typeset \emph{after} punctuation
-marks.\footnote{As in this example.}
-
-\subsection{Figures}
-
-All artwork must be neat, clean, and legible. Lines should be dark
-enough for purposes of reproduction. The figure number and caption
-always appear after the figure. Place one line space before the figure
-caption and one line space after the figure. The figure caption should
-be lower case (except for first word and proper nouns); figures are
-numbered consecutively.
-
-You may use color figures.  However, it is best for the figure
-captions and the paper body to be legible if the paper is printed in
-either black/white or in color.
-\begin{figure}[h]
-  \centering
-  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
-  \caption{Sample figure caption.}
-\end{figure}
-
-\subsection{Tables}
-
-All tables must be centered, neat, clean and legible.  The table
-number and title always appear before the table.  See
-Table~\ref{sample-table}.
-
-Place one line space before the table title, one line space after the
-table title, and one line space after the table. The table title must
-be lower case (except for first word and proper nouns); tables are
-numbered consecutively.
-
-Note that publication-quality tables \emph{do not contain vertical
-  rules.} We strongly suggest the use of the \verb+booktabs+ package,
-which allows for typesetting high-quality, professional tables:
-\begin{center}
-  \url{https://www.ctan.org/pkg/booktabs}
-\end{center}
-This package was used to typeset Table~\ref{sample-table}.
-
-\begin{table}[t]
-  \caption{Sample table title}
-  \label{sample-table}
-  \centering
-  \begin{tabular}{lll}
-    \toprule
-    \multicolumn{2}{c}{Part}                   \\
-    \cmidrule{1-2}
-    Name     & Description     & Size ($\mu$m) \\
-    \midrule
-    Dendrite & Input terminal  & $\sim$100     \\
-    Axon     & Output terminal & $\sim$10      \\
-    Soma     & Cell body       & up to $10^6$  \\
-    \bottomrule
-  \end{tabular}
-\end{table}
-
-\section{Final instructions}
-
-Do not change any aspects of the formatting parameters in the style
-files.  In particular, do not modify the width or length of the
-rectangle the text should fit into, and do not change font sizes
-(except perhaps in the \textbf{References} section; see below). Please
-note that pages should be numbered.
-
-\section{Preparing PDF files}
-
-Please prepare submission files with paper size ``US Letter,'' and
-not, for example, ``A4.''
-
-Fonts were the main cause of problems in the past years. Your PDF file
-must only contain Type 1 or Embedded TrueType fonts. Here are a few
-instructions to achieve this.
-
-\begin{itemize}
-
-\item You should directly generate PDF files using \verb+pdflatex+.
-
-\item You can check which fonts a PDF files uses.  In Acrobat Reader,
-  select the menu Files$>$Document Properties$>$Fonts and select Show
-  All Fonts. You can also use the program \verb+pdffonts+ which comes
-  with \verb+xpdf+ and is available out-of-the-box on most Linux
-  machines.
-
-\item The IEEE has recommendations for generating PDF files whose
-  fonts are also acceptable for NIPS. Please see
-  \url{http://www.emfield.org/icuwb2010/downloads/IEEE-PDF-SpecV32.pdf}
-
-\item \verb+xfig+ "patterned" shapes are implemented with bitmap
-  fonts.  Use "solid" shapes instead.
-
-\item The \verb+\bbold+ package almost always uses bitmap fonts.  You
-  should use the equivalent AMS Fonts:
-\begin{verbatim}
-   \usepackage{amsfonts}
-\end{verbatim}
-followed by, e.g., \verb+\mathbb{R}+, \verb+\mathbb{N}+, or
-\verb+\mathbb{C}+ for $\mathbb{R}$, $\mathbb{N}$ or $\mathbb{C}$.  You
-can also use the following workaround for reals, natural and complex:
-\begin{verbatim}
-   \newcommand{\RR}{I\!\!R} %real numbers
-   \newcommand{\Nat}{I\!\!N} %natural numbers
-   \newcommand{\CC}{I\!\!\!\!C} %complex numbers
-\end{verbatim}
-Note that \verb+amsfonts+ is automatically loaded by the
-\verb+amssymb+ package.
-
-\end{itemize}
-
-If your file contains type 3 fonts or non embedded TrueType fonts, we
-will ask you to fix it.
-
-\subsection{Margins in \LaTeX{}}
-
-Most of the margin problems come from figures positioned by hand using
-\verb+\special+ or other commands. We suggest using the command
-\verb+\includegraphics+ from the \verb+graphicx+ package. Always
-specify the figure width as a multiple of the line width as in the
-example below:
-\begin{verbatim}
-   \usepackage[pdftex]{graphicx} ...
-   \includegraphics[width=0.8\linewidth]{myfile.pdf}
-\end{verbatim}
-See Section 4.4 in the graphics bundle documentation
-(\url{http://mirrors.ctan.org/macros/latex/required/graphics/grfguide.pdf})
-
-A number of width problems arise when \LaTeX{} cannot properly
-hyphenate a line. Please give LaTeX hyphenation hints using the
-\verb+\-+ command when necessary.
-
-\subsubsection*{Acknowledgments}
-
-Use unnumbered third level headings for the acknowledgments. All
-acknowledgments go at the end of the paper. Do not include
-acknowledgments in the anonymized submission, only in the final paper.
-
 \section*{References}
-
-References follow the acknowledgments. Use unnumbered first-level
-heading for the references. Any choice of citation style is acceptable
-as long as you are consistent. It is permissible to reduce the font
-size to \verb+small+ (9 point) when listing the references. {\bf
-  Remember that you can use a ninth page as long as it contains
-  \emph{only} cited references.}
-\medskip
 

### 2017-04-27 paper_final.tex
Wrote algorithm for bounding etat

@@
 \usepackage{parskip}
+\usepackage{amssymb}
+\usepackage{amsmath}
+\usepackage{color}
 
@@
 }
+
+\newcommand{\learn}{\mathcal{A}_{w_0}^\eta}
 
@@
 \section{Teaching Dimension}
+\cite{perceptron} used two metrics when analyzing their teaching strategies. The first was the exact 
+teaching dimension. The exact teaching dimension is the length of the shortest training sequence that 
+teaches a learner the desired concept.
+
+\subsection{$TD_{exact}$}
+
+Formally, let $\mathbb{S}$ be the space of finite training 
+sequences. Then let $\mathcal{A}_{w_0}^{\eta} : \mathbb{S} \to \mathbb{R}^d$ be a function the gives the 
+resultant weight vector after training on a sequence in $\mathbb{S}$, where $w_0$ is the initial weight 
+vector, and $\eta$ is the learning rate.
+Then if the teacher which to teach a concept $w^*$, then since $w^*$ describes a linear decision boundary then for any $c > 0$, $cw^*$ is parameterizes the same concept as $w^*$
+so the exact teaching dimension is 
+$$
+TD_{exact}(w^*, \mathcal{A}_{w_0}^\eta) = \min\{ \lvert S \rvert : 
+\mathcal{A}_{w_0}^\eta(S) = cw^* \text{ for some } c >0 \}
+$$
+
+\cite{perceptron} showed that when $\eta$ and $w_0$ where known, $TD_{exact}(w^*, \mathcal{A}_{w_0}^\eta) = 1$
+
+\subsection{$TD_\epsilon$}
+\cite{perceptron} also defined an approximate teaching dimension for cases where the exact teaching dimension was infinite but one could approximately teach a concept within $\epsilon$ distance.
+For perceptrons, the distance metric used was simply the 1 minus the cosine angle between $w^*$
+and $\learn(S)$
+$$
+1 -\frac{\langle \learn(S), w^* \rangle}{\lVert \learn(s) \rVert \lVert w^* \rVert} \leq \epsilon
+$$
+
+Then let $\mathbb{T}_\epsilon$ be the set of $\epsilon-\text{approximate}$ teaching strategies for a decision boundary $w^*$. Then
+$$
+TD_\epsilon(w^*, \learn) = \min_{t \in 
+\mathbb{T}_\epsilon} \max_{w_0 \in 
+\mathbb{R}^d} \lvert t(w_0) \rvert
+$$
+
+\cite{perceptron} showed that when $w_0$ was unknown but $\eta$ was known $TD_\epsilon(w^*, \learn) = 3$
+
+\section{Approximate Teaching with Unkown $\eta$}
+Now we look at the scenario where the initial weight vector is known but the learning rate is unknown and bounded.
+
+\subsection{Using Unlabeled Examples}
+Before the teaching dimension was only analyzed with labeled examples.
+Here we relax this constraint and allow unlabeled examples to be used in the teaching sequence.
+Now we redefine $\mathbb{S}$ to be the set of all sequences of labeled and unlabeled examples.
+And for any $S \in \mathbb{S}$
+$$
+\learn(S) = \learn(S \setminus \{s \in S : s = (x, ?)\} )
+$$
+
+\subsection{Algorithm for bounding $\eta$}
+With the ability to teach with unlabeled examples, below shows the optimal algorithm for bounding $\eta$ within a desired length, under the conditions that $\eta$ is bounded and $w_0$ is known a priori.
+
+\begin{algorithm}
+\caption{Bounding $\eta$ within $\epsilon$ }
+\begin{algorithmic}[1]
+	\REQUIRE $\epsilon$ , lower bound $\eta_{\min} > 0$, upper bound $\eta_{\max} < \infty$ and $w^*$
+	\STATE Select $(x_1 , y_1)$ s.t. $sign(\langle w^* , x_1 \rangle) = y_1 = 1 = 
+	-sign(\langle w_0 , x_1 \rangle )$
+	\STATE Give $(x_1, y_1)$ to the perceptron and allow to update.
+	\STATE $\alpha \leftarrow \eta_{\min}$
+	\STATE $\beta \leftarrow \eta_{\max}$
+
+	\WHILE{$\beta - \alpha > \epsilon$}
+		\STATE Select $ x_2$ s.t. $\langle w_0 , x_2 \rangle \neq 0, \langle x_1 , x_2 \rangle \neq 0$ and $\langle w_0, x_2 \rangle \frac{\beta - \alpha}{2}\langle x_1, x_2 \rangle = 0$
+		\STATE Let the perceptron predict $\hat{y}$ for $x_2$
+		\IF{$\hat{y} = 1$}
+			\STATE $ \alpha \leftarrow \frac{\beta - \alpha}{2}$ 		
+		\ELSE
+			\STATE $ \beta \leftarrow \frac{\beta - \alpha}{2}$ 
+		\ENDIF	
+	\ENDWHILE   
+	\RETURN $(\alpha , \beta)$
+\end{algorithmic}
+\end{algorithm}
+
+\section*{Theorem 1}
+If given a perceptron with known starting parameter $w_0$, desired parameter $w^*$, and unknown learning rate $\eta \in [\alpha , \beta]$ for given $\epsilon > 0$, we can guarantee $\eta \in [\alpha', \beta']$ such that $\beta' - \alpha' \leq \epsilon$ using $1 + \lceil \log_2(\frac{\beta - \alpha}{\epsilon})\rceil$ examples.=
+
+\subsection*{Proof:}
+Assume $w_0 \neq cw^*$ for arbitrary $c > 0$, then there exists an $(x_1, y_1)$ such that $\text{sign}(\langle w^*,x_1 \rangle) = y_1 = 1$ and $\text{sign}(\langle w_0,x_1 \rangle) = -y_1$.
+\color{red}
+I don't think that its hard to show this is true.
+\color{black}
+
+Then give $(x_1, y_1)$ to the learner and then after training update,
+$$
+w_1 = w_0 + \eta* x_1
+$$
+
+Then grab an unlabeled $x_2$ such that
+$\langle w_0,x_2 \rangle \neq 0$, $\langle x_1, x_2 \rangle \neq 0$
+and 
+$$
+\langle w_0,x_2 \rangle + \frac{\beta - \alpha}{2} \langle x_1, x_2 \rangle = 0
+$$
+\color{red}
+I'm a moron. What's the closed form of this? I know there is not a unique solution. We just need the simplest one.
+\color{black}
+
+Then probe the learner with $x_2$. If the learner outputs $+1$ then
+$\eta \in (\frac{\beta - \alpha}{2} , \beta]$, else 
+$\eta \in [\alpha,\frac{\beta - \alpha}{2}]$
 

### 2017-04-28 paper_final.tex
Got the proof on simple problem in

@@
 
-\section*{Theorem 1}
-If given a perceptron with known starting parameter $w_0$, desired parameter $w^*$, and unknown learning rate $\eta \in [\alpha , \beta]$ for given $\epsilon > 0$, we can guarantee $\eta \in [\alpha', \beta']$ such that $\beta' - \alpha' \leq \epsilon$ using $1 + \lceil \log_2(\frac{\beta - \alpha}{\epsilon})\rceil$ examples.=
+\textbf{Theorem 1.}
+\textit{
+If given a perceptron with known starting parameter $w_0$, desired parameter $w^*$, and unknown 
+learning rate $\eta \in [\eta_{\min} , \eta_{\max}]$, then for given $\epsilon > 0$, \textbf{Algorithm 2} can guarantee $\eta \in 
+[\alpha, \beta]$ such that $\beta - \alpha \leq \epsilon$ using $1 + \lceil \log_2(\frac{\eta_
+{\min} - \eta_{\max}}{\epsilon})\rceil$ examples.}
 
-\subsection*{Proof:}
+\textit{Proof.}
 Assume $w_0 \neq cw^*$ for arbitrary $c > 0$, then there exists an $(x_1, y_1)$ such that $\text{sign}(\langle w^*,x_1 \rangle) = y_1 = 1$ and $\text{sign}(\langle w_0,x_1 \rangle) = -y_1$.
 \color{red}
-I don't think that its hard to show this is true.
+I don't think that its hard to show this is true. But I won't prove for now
 \color{black}
@@
 $$
-w_1 = w_0 + \eta* x_1
+w_1 = w_0 + \eta x_1
 $$
@@
 $$
-\langle w_0,x_2 \rangle + \frac{\beta - \alpha}{2} \langle x_1, x_2 \rangle = 0
+\langle w_0,x_2 \rangle + \frac{\eta_{\max} - \eta_{\min}}{2} \langle x_1, x_2 \rangle = 0
 $$
 \color{red}
-I'm a moron. What's the closed form of this? I know there is not a unique solution. We just need the simplest one.
+There should always be at least one solution to this. Again I won't prove for now.
 \color{black}
@@
 Then probe the learner with $x_2$. If the learner outputs $+1$ then
-$\eta \in (\frac{\beta - \alpha}{2} , \beta]$, else 
-$\eta \in [\alpha,\frac{\beta - \alpha}{2}]$
+$\eta \in (\frac{\eta_{\max} - \eta_{\min}}{2} , \eta_{\max}]$, else 
+$\eta \in [\eta_{\min},\frac{\eta_{\max} - \eta_{\min}}{2}]$
+
+After the first labeled example , the length of the bound on $\eta$ is halved which each unlabeled example given.
+So one can see that with $n + 1$ examples the length of the bound on $\eta$ is $\frac{\eta_{\max} - \eta_{\min}}{2 ^ n }$.
+So to achieve a bound length of $\epsilon$ one needs
+$ 1 + \lceil \log_2 ( \frac{\eta_
+{\min} - \eta_{\max}}{\epsilon} ) \rceil$ examples.
+
+\subsection{Teaching Dimension for Unknown $\eta$}
+
+\textbf{Theorem 2.}
+\textit{ If $w_0$ is known and $ 0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ 
+then $\mathbb{T}_{\epsilon}(w^*, \learn)  \leq 2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$
+}
+\\
+\\
+\\
+\textit{Proof.}
+Assume WLOG $\lVert w^* \rVert = 1$.
+
+Pick $(x_1,y_1)$ such that $y_1 = -1$, $\lVert x_1 \rVert = \frac{2 \lVert w_0 \rVert}{\epsilon \eta_{\min}}$ and $\langle x_1 , w^* \rangle = 0$.
+
+Use this $(x_1, y_1)$ in \textbf{Algorithm 2} to get a bound on $\eta$ such that $\eta \in [\alpha , \beta]$ and $\beta - \alpha <= 2\epsilon \eta_{\max}$
+
+Then let $x_2 = \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2}w^* + x_1$.
+It should be clear that then that $sign(\langle w* , x_2 \rangle) =  y_2 = 1$
+
+Then realize that
+$w_1 = w_0 - \eta x_1$
+
+So
+$$
+y_2 \langle w_1, x_2 \rangle  = \bigg\langle \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0 - \eta x_1 \bigg\rangle
+$$
+$$
+= \bigg\langle \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0  \bigg\rangle - \eta \lVert x_1 \rVert^2
+$$
+$$
+\leq \bigg( \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} \lVert w^* \rVert + \lVert x_1 \rVert \bigg ) \lVert w_0 \rVert - \eta \lVert x_1 \rVert^2
+$$
+$$
+= \frac{2 \lVert w_0 \rVert^2}{\epsilon (\beta + \alpha)/2} + \frac{2 \lVert w_0 \rVert ^2}{\epsilon \eta_{\min}} - \eta \frac{4 \lVert w_0 \rVert^2}{\epsilon^2 \eta_{\min}^2}
+$$
+$$
+\leq \frac{4 \lVert w_0 \rVert^2}{\epsilon (\beta + \alpha)/2}  -  \frac{4 \lVert w_0 \rVert^2}{\epsilon^2 \eta_{\min}}
+$$
+which is less than $0$ for $\epsilon < 1$, so $(x_2 , y_2)$ will cause the perceptron to update.
+
+Then,
+notice that $w_2 = w_0 +\eta \frac{2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} w^*$
+
+Then 
+$$
+\frac{\langle w_2, w^* \rangle}{\lVert w_1 \rVert \lVert w^* \rVert} = \frac{
+\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} \lVert w^* \lVert ^2 + \langle w_0, w^* \rangle}{\lVert w_2 \rVert}
+$$ 
+$$
+\geq \frac{\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} - \lVert w_0 \rVert}{\lVert w_0 \rVert +\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} }
+$$
+$$
+= 1 - \frac{2 \lVert w_0  \rVert}{\lVert w_0 \rVert +\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} }
+$$
+$$
+= 1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{\eta 2  \lVert w_0 \rVert}{(\beta + \alpha)/2} } \epsilon
+$$
+$$
+\geq  1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{\eta 2  \lVert w_0 \rVert}{\eta_{\max} - (\beta - \alpha) / 2} } \epsilon
+$$
+$$
+\geq  1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{\eta 2  \lVert w_0 \rVert}{\eta_{\max} (1-\epsilon)} } \epsilon
+$$
+$$
+\geq 1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{ 2  \lVert w_0 \rVert}{(1-\epsilon)} } \epsilon
+$$
+$$
+\geq 1 - \epsilon
+$$
+
+Therefore 
+$T_\epsilon \leq  2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$
 

### 2017-04-29 paper_final.tex
Fixed small issue with proof. y should be -1 instead of 1 for x1

@@
 	\REQUIRE $\epsilon$ , lower bound $\eta_{\min} > 0$, upper bound $\eta_{\max} < \infty$ and $w^*$
-	\STATE Select $(x_1 , y_1)$ s.t. $sign(\langle w^* , x_1 \rangle) = y_1 = 1 = 
+	\STATE Select $(x_1 , y_1)$ s.t. $sign(\langle w^* , x_1 \rangle) = y_1 = -1 = 
 	-sign(\langle w_0 , x_1 \rangle )$
@@
 	\WHILE{$\beta - \alpha > \epsilon$}
-		\STATE Select $ x_2$ s.t. $\langle w_0 , x_2 \rangle \neq 0, \langle x_1 , x_2 \rangle \neq 0$ and $\langle w_0, x_2 \rangle \frac{\beta - \alpha}{2}\langle x_1, x_2 \rangle = 0$
+		\STATE Select $ x_2$ s.t. $\langle w_0 , x_2 \rangle \neq 0, \langle x_1 , x_2 \rangle \neq 0$ and $\langle w_0, x_2 \rangle - \frac{\beta - \alpha}{2}\langle x_1, x_2 \rangle = 0$
 		\STATE Let the perceptron predict $\hat{y}$ for $x_2$
 		\IF{$\hat{y} = 1$}
+			\STATE $ \beta \leftarrow \frac{\beta - \alpha}{2}$ 		
+		\ELSE
 			\STATE $ \alpha \leftarrow \frac{\beta - \alpha}{2}$ 
-		\ELSE
-			\STATE $ \beta \leftarrow \frac{\beta - \alpha}{2}$ 
 		\ENDIF	
@@
 \textit{Proof.}
-Assume $w_0 \neq cw^*$ for arbitrary $c > 0$, then there exists an $(x_1, y_1)$ such that $\text{sign}(\langle w^*,x_1 \rangle) = y_1 = 1$ and $\text{sign}(\langle w_0,x_1 \rangle) = -y_1$.
+Assume $w_0 \neq cw^*$ for arbitrary $c > 0$, then there exists an $(x_1, y_1)$ such that $\text{sign}(\langle w^*,x_1 \rangle) = y_1 = -1$ and $\text{sign}(\langle w_0,x_1 \rangle) = -y_1$.
 \color{red}
@@
 $$
-\langle w_0,x_2 \rangle + \frac{\eta_{\max} - \eta_{\min}}{2} \langle x_1, x_2 \rangle = 0
+\langle w_0,x_2 \rangle - \frac{\eta_{\max} - \eta_{\min}}{2} \langle x_1, x_2 \rangle = 0
 $$
@@
 
-Then probe the learner with $x_2$. If the learner outputs $+1$ then
+Then probe the learner with $x_2$. If the learner outputs $-1$ then
 $\eta \in (\frac{\eta_{\max} - \eta_{\min}}{2} , \eta_{\max}]$, else 

### 2017-05-03 paper_final.tex
Finished liar proof

@@
 
-\usepackage[utf8]{inputenc} % allow utf-8 input
-\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
-\usepackage{hyperref}       % hyperlinks
-\usepackage{url}            % simple URL typesetting
-\usepackage{booktabs}       % professional-quality tables
 \usepackage{amsfonts}       % blackboard math symbols
-\usepackage{nicefrac}       % compact symbols for 1/2, etc.
-\usepackage{microtype}      % microtypography
 \usepackage{algorithm}
 \usepackage{algorithmic}
-\usepackage{bbm}
-\usepackage{parskip}
 \usepackage{amssymb}
@@
 \usepackage{color}
+\usepackage{bbm}
 
@@
 \newcommand{\learn}{\mathcal{A}_{w_0}^\eta}
+\newcommand{\radian}{\text{radian}}
 
@@
 Therefore 
-$T_\epsilon \leq  2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$
+$\mathbb{T}_\epsilon \leq  2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$
+
+\section{Teaching Dimension for unknown $\eta$ and $w_0$}
+Here we show a strategy where we know neither the learning rate or the initial weight vector of our perceptron learner.
+With prior knowledge of some reasonable bound on the magnitude of $w_0$ and $\eta$, we show a strategy that gives an upper bound on the approximate teaching dimension in this scenario.
+
+\subsection{Ability to Lie}
+Allowing the teacher to lie, or give $(x,y)$ that disagree with $w^*$, make teaching the learner very easy. In fact in this scenario, the approximate teaching dimension is $2$.
+\\
+\\
+\\
+\textbf{Theorem 5.} \textit{
+Let $w_0$, $\eta$ be unknown with $\lVert w_0 \rVert \leq b$ and $0 < \eta_{\min} \leq \eta$.
+Then with the ability to lie, $\mathbb{T}_{\epsilon}(w^*, \learn) = 2$
+}
+\\
+\\
+\\
+\textit{Proof.}
+WLOG assume $\lVert w^* \rVert = 1$
+Select an $x_1 = \frac{b(2-\epsilon)}{\eta_{\min} \epsilon}w^*, \qquad y_1 = -1$
+Then give $(x_1 , y _1)$ to the perceptron.
+Then let $x_2 = 2x_1, \qquad y_2 = 1$ and give $(x_2, y_2)$ to the perceptron.
+
+Then there are two cases.
+
+\textbf{Case 1:} The perceptron incorrectly predicts $y = 1$ for $x_1$.
+
+Then 
+$
+w_1 = w_0 - \frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon}w^*
+$
+
+Then 
+$$y_2 \langle w_1, 2x_1 \rangle
+$$
+$$
+ = \langle w_0, 2x_1 \rangle - 2\frac{(\eta b(2-\epsilon))^2}{(\eta_{\min}\epsilon)^2}
+ \leq 2b\frac{\eta b(2-\epsilon)}{\eta_{\min}\epsilon}
+-  2\frac{(\eta b(2-\epsilon))^2}{(\eta_{\min}\epsilon)^2} 
+$$
+$$
+\leq 2\frac{\eta b^2(2-\epsilon)}{\eta_{\min}\epsilon}
+-  2\frac{\eta (b(2-\epsilon))^2}{\eta_{\min}\epsilon^2}
+< 0 \qquad \text{ for } \epsilon < 0
+$$
+Therefore $(x_2, y_2)$ causes and update and
+$w_2 =  w_0 + \frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon}w^* $
+
+Then
+$$
+\frac{\langle w_2 , w^* \rangle}{\lVert w_2 \rVert \lVert w^* \rVert} = \frac{\frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon} + \langle w_0, w^* \rangle}{\lVert w_2 \rVert} \geq \frac{\frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon} - b}{b + \frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon}}
+$$
+Which implies
+$$
+1 - \frac{\langle w_2 , w^* \rangle}{\lVert w_2 \rVert \lVert w^* \rVert} \leq \frac{2b}{b + \frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon}}
+\leq
+\frac{2}{1 + \frac{2-\epsilon}{\epsilon}} = \epsilon
+$$
+
+\textbf{Case 2:} $(x_1, y_1)$ does not cause an update.
+
+Then clearly $(x_2, y_2)$ will cause an update and
+$$
+w_2 = w_0 + 2\frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon}w^* 
+$$
+so,
+$$
+\frac{\langle w_2 , w^* \rangle}{\lVert w_2 \rVert \lVert w^* \rVert} = 2\frac{\frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon} + \langle w_0, w^* \rangle}{\lVert w_2 \rVert} \geq \frac{\frac{\eta b(2-\epsilon)}{\eta_{\min} \epsilon} + \langle w_0, w^* \rangle}{\lVert w_2 \rVert} \geq 1 - \epsilon
+$$
+
+We have thus shown that we can get an $\epsilon$ approximate bound with only 2 examples.
+It should be clear that this is impossible to do with $1$ example since without knowledge of $w_0$ there exists no $(x_1, y_1)$ that can guarantee the perceptron will update.
+
+So 
+$
+\mathbb{T}_{\epsilon}(w^*, \learn) = 2
+$
+
+\textbf{Corrolary}
+\textit{
+Theorem 5 also shows that with known $\eta$ and ability to lie the approximate teaching dimension is still 2.
+This is 1 less the the $\epsilon$ approximate Teaching dimension where we cannot lie.
+\cite{perceptron}
+}
 

### 2017-05-03 paper_final.tex
Finished final part of hardest version. Still need Gabe to figure out what the number of examples needed for bounding is

@@
 \textbf{Theorem 2.}
-\textit{ If $w_0$ is known and $ 0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ 
+\textit{ If $w_0$ is known , $w_0 \leq b < \infty$ and $ 0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ 
 then $\mathbb{T}_{\epsilon}(w^*, \learn)  \leq 2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$
@@
 
-Pick $(x_1,y_1)$ such that $y_1 = -1$, $\lVert x_1 \rVert = \frac{2 \lVert w_0 \rVert}{\epsilon \eta_{\min}}$ and $\langle x_1 , w^* \rangle = 0$.
+Pick $(x_1,y_1)$ such that $y_1 = -1$, $\lVert x_1 \rVert = \frac{2 b}{\epsilon \eta_{\min}}$ and $\langle x_1 , w^* \rangle = 0$.
 
@@
 
-Then let $x_2 = \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2}w^* + x_1$.
+Then let $x_2 = \frac{2 b}{\epsilon (\beta + \alpha)/2}w^* + x_1$.
 It should be clear that then that $sign(\langle w* , x_2 \rangle) =  y_2 = 1$
@@
 $$
-y_2 \langle w_1, x_2 \rangle  = \bigg\langle \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0 - \eta x_1 \bigg\rangle
+y_2 \langle w_1, x_2 \rangle  = \bigg\langle \frac{2 b}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0 - \eta x_1 \bigg\rangle
 $$
 $$
-= \bigg\langle \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0  \bigg\rangle - \eta \lVert x_1 \rVert^2
+= \bigg\langle \frac{2 b}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0  \bigg\rangle - \eta \lVert x_1 \rVert^2
 $$
 $$
-\leq \bigg( \frac{2 \lVert w_0 \rVert}{\epsilon (\beta + \alpha) /2} \lVert w^* \rVert + \lVert x_1 \rVert \bigg ) \lVert w_0 \rVert - \eta \lVert x_1 \rVert^2
+\leq \bigg( \frac{2 b}{\epsilon (\beta + \alpha) /2} \lVert w^* \rVert + \lVert x_1 \rVert \bigg ) b - \eta \lVert x_1 \rVert^2
 $$
 $$
-= \frac{2 \lVert w_0 \rVert^2}{\epsilon (\beta + \alpha)/2} + \frac{2 \lVert w_0 \rVert ^2}{\epsilon \eta_{\min}} - \eta \frac{4 \lVert w_0 \rVert^2}{\epsilon^2 \eta_{\min}^2}
+\leq \frac{4 b ^2}{\epsilon \eta_{\min}} - \eta \frac{4 b^2}{\epsilon^2 \eta_{\min}^2}
 $$
 $$
-\leq \frac{4 \lVert w_0 \rVert^2}{\epsilon (\beta + \alpha)/2}  -  \frac{4 \lVert w_0 \rVert^2}{\epsilon^2 \eta_{\min}}
+\leq \frac{4 b^2}{\epsilon \eta_{\min}}  -  \frac{4 b^2}{\epsilon^2 \eta_{\min}}
 $$
@@
 Then,
-notice that $w_2 = w_0 +\eta \frac{2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} w^*$
+notice that $w_2 = w_0 +\eta \frac{2  b}{\epsilon (\beta + \alpha)/2} w^*$
 
@@
 $$
-\frac{\langle w_2, w^* \rangle}{\lVert w_1 \rVert \lVert w^* \rVert} = \frac{
-\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} \lVert w^* \lVert ^2 + \langle w_0, w^* \rangle}{\lVert w_2 \rVert}
+\frac{\langle w_2, w^* \rangle}{\lVert w_2 \rVert \lVert w^* \rVert} = \frac{
+\frac{\eta 2  b}{\epsilon (\beta + \alpha)/2} \lVert w^* \lVert ^2 + \langle w_0, w^* \rangle}{\lVert w_2 \rVert}
 $$ 
 $$
-\geq \frac{\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} - \lVert w_0 \rVert}{\lVert w_0 \rVert +\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} }
+\geq \frac{\frac{\eta 2  b}{\epsilon (\beta + \alpha)/2} - b}{b +\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} }
 $$
 $$
-= 1 - \frac{2 \lVert w_0  \rVert}{\lVert w_0 \rVert +\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} }
+= 1 - \frac{2 b}{b +\frac{\eta 2  b}{\epsilon (\beta + \alpha)/2} }
 $$
 $$
-= 1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{\eta 2  \lVert w_0 \rVert}{(\beta + \alpha)/2} } \epsilon
+= 1 - \frac{2b}{b \epsilon + \frac{\eta 2  b}{(\beta + \alpha)/2} } \epsilon
 $$
 $$
-\geq  1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{\eta 2  \lVert w_0 \rVert}{\eta_{\max} - (\beta - \alpha) / 2} } \epsilon
+\geq  1 - \frac{2b}{b \epsilon + \frac{\eta 2  b}{\eta_{\max} - (\beta - \alpha) / 2} } \epsilon
 $$
 $$
-\geq  1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{\eta 2  \lVert w_0 \rVert}{\eta_{\max} (1-\epsilon)} } \epsilon
+\geq  1 - \frac{2b}{b \epsilon + \frac{\eta 2  b}{\eta_{\max} (1-\epsilon)} } \epsilon
 $$
 $$
-\geq 1 - \frac{2\lVert w_0 \rVert}{\lVert w_0  \rVert \epsilon + \frac{ 2  \lVert w_0 \rVert}{(1-\epsilon)} } \epsilon
+\geq 1 - \frac{2b}{b \epsilon + \frac{ 2  b}{(1-\epsilon)} } \epsilon
 $$
@@
 With prior knowledge of some reasonable bound on the magnitude of $w_0$ and $\eta$, we show a strategy that gives an upper bound on the approximate teaching dimension in this scenario.
+
+\textbf{Theorem 4.} 
+\textit{With unknown $w_0$ such that $\lVert w_0 \rVert \leq b < \infty$
+and unknown $\eta$ such that $0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ then 
+$
+\mathbb{T}_\epsilon(w^* , \learn) \leq 3 + ?
+$
+}
+\\
+\\
+\\
+\textit{Proof.}
+First using \textbf{Algorithm 3} bound $\eta$ such that $ \alpha \leq \eta \leq \beta$ and $\beta - \alpha \leq 2\epsilon \eta_{\max}$
+
+Then WLOG assume $\lVert w^8 \rVert = 1$. Then pick an $x_1$ such that 
+$\lVert x_1 \rVert = \frac{2b}{\epsilon (\beta + \alpha)/2}$ and $\langle w^*, x_1 \rangle = 0$.
+Such an $x_1$ always exists.
+Then, let $x'_1 = -x_1.$ Then $y_1 = y'_1 = \text{sign}(\langle w*, x_1 \rangle) = -1$.
+Then since $y_1 = y'_1$ then the perceptron must make an error on one of the examples.
+So first give $(x_1, y_1)$ to the perceptron.
+\underline{Case 1}: If $(x_1, y_1)$ then $w_1 = w_0 - \eta x_1$. 
+Then select at the second iteration an $x_2 = \frac{2b}{\epsilon (\beta + \alpha)/2}$. Using the same logic from theorem 2, we can see that this will give us our desired $\epsilon$ approximate $w_2$.
+
+\underline{Case 2}: If $(x_1, y_1)$ did not cause and update then set $x_2 = x'_1$ , $y_2 = y'_1$ and $x_3 = \frac{2b}{\epsilon (\beta + \alpha)/2}w^* + x_2$.
+Using very similar logic to how Case 1 used Theorem 2, we can see that this will also get us the desired $\epsilon$ approximate $w_3$.
+
+In Case 1 we require 2 examples and and Case 2 we require 3, so including the examples needed to bound $\eta$ we get that 
+$$
+\mathbb{T}_\epsilon(w^*, \learn) \leq 3 + ?
+$$
 

### 2017-05-04 paper_final.tex
small change
Added more recent references

@@
 This constructive task is known as optimal teaching \cite{machine_teaching} \cite{teaching_dimension}.
-\cite{perceptron} looked for the first time at online teaching in an online environment, with an online perceptron.
+It has applications in education and security \cite{security}\cite{education} \cite{poisoning}.
+\cite{perceptron}\cite{td_linear} looked for the first time at online teaching in an online environment, with an online perceptron.
 In this paper we look at optimal teaching of the same perceptron, but now we give the teacher the ability to use unlabeled examples.

### 2017-05-04 paper_final.tex
my stuff

--- 2017-05-03 paper_final.tex
@@
 
+\usepackage[utf8]{inputenc} % allow utf-8 input
+\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
+\usepackage{hyperref}       % hyperlinks
+\usepackage{url}            % simple URL typesetting
+\usepackage{booktabs}       % professional-quality tables
 \usepackage{amsfonts}       % blackboard math symbols
@@
 \usepackage{color}
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
 \usepackage{bbm}
@@
 \begin{abstract}
-  Optimal teaching is the task of constructing a special efficient training set, which when given to a learner teaches the desired concept inside the learners concept class.
-Before \cite{perceptron}, analysis of optimal teaching was only focused on batch learners.
-\cite{perceptron} looked at the optimal teaching strategy of an online Perceptron in two different scenarios with varying degrees of knowledge of the initial state of the learner.
-In this paper we show extensions of these scenarios where knowledge of the initial state is even more unknown.
+  Optimal teaching is the task of constructing an efficient training set
+  that teaches a learner some desired concept inside its concept class. Before
+  \cite{perceptron}, analysis of optimal teaching was only focused on batch
+  learners. \cite{perceptron} looked at the optimal teaching strategy of an
+  online Perceptron with varying degrees of knowledge of the initial state of
+  the learner. In this paper, we extend these results to environments where
+  there is even less knowledge of the Perceptron's initial state, but the
+  teacher is given extra powers to compensate. We present an efficient algorithm
+  to force the learner into a desired state with no knowledge of the learner's
+  initial state. We also analyze a setting in which a teacher has the ability to
+  lie.
 \end{abstract}
@@
 \section{Introduction}
-There may be a scenario where one entity, or the \textit{teacher},  has a desired target concept and a learner in which the teacher wants to embed that concept.
-In this scenario the teacher can only interact with the learner by constructing and then giving the learner a set of training examples.
-This constructive task is known as optimal teaching \cite{machine_teaching} \cite{teaching_dimension}.
-\cite{perceptron} looked for the first time at online teaching in an online environment, with an online perceptron.
-In this paper we look at optimal teaching of the same perceptron, but now we give the teacher the ability to use unlabeled examples.
-Unlabeled examples allow the teacher to probe to discover more about the learners current state while not changing the learner.
-We show that this new added ability allows the teacher to teach an online perceptron in a scenario, that before may have been difficult.
+In the real world, there are often scenarios where a teacher wishes to
+embed a desired concept within a learner. Sometimes, the teacher can only
+interact with the learner by providing the learner with a set of training examples.
+The task of creating the smallest possible set of examples that
+produces the desired concept in the learner is known as optimal teaching
+\cite{machine_teaching} \cite{teaching_dimension}. \cite{perceptron} looked for
+the first time at optimal teaching in an online environment by proving the
+optimal teaching dimension in an online Perceptron. In this paper we look at the
+optimal teaching of the same perceptron, but with a teacher that also possess
+the ability to use unlabeled examples. An unlabeled example gives the teacher
+knowledge of the learner's prediction about that example without altering the
+learner's state. This is a reasonable power for any real-world teacher to
+posses. We show that this added ability allows the teacher to teach an
+online perceptron in a zero-knowledge scenario that otherwise would have been
+difficult.
 
-The specific perceptron we are teaching is the  online perceptron \cite{perceptron_algo}. The algorithm is designed for a binary classification. It can learn any linear decision boundary,
-with mapping $x \to sign(\langle w, x \rangle)$ where $x \in \mathbb{R}^d$ comes from the input space and $w \in \mathbb{R}^d$ parameterizes the perceptron.
-Here , as in \cite{perceptron}, $sign(0) = -1$ for completeness.
-The learning algorithm for the online perceptron is seen below.
+The specific perceptron we are teaching is the online perceptron
+designed for binary classification \cite{perceptron_algo}. It can learn any
+linear decision boundary with mapping $x \to sign(\langle w, x \rangle)$, where
+$x \in \mathbb{R}^d$ is in the input space and $w \in \mathbb{R}^d$
+parameterizes the perceptron. Here, as in \cite{perceptron}, $sign(0) = -1$ for
+completeness. The learning algorithm for the online perceptron is seen below.
 
@@
 
-As one can see, knowledge of $w_0$ and $\eta$ are critical to being able to teach an online perceptron learner.
-\cite{perceptron} looked at teaching a perceptron with and without knowledge of $w_0$.
-Here we look at the situation when the learning rate $\eta$ is unknown.
-As well we look at the most challenging case, when both $w_0$ and $\eta$ are unknown at the start of teaching.
+Because $w_0$ and $\eta$ affect the Perceptron's learning, knowledge of them is
+critical to being able to teach an online Perceptron learner. \cite{perceptron}
+looked at teaching a perceptron with, and without knowledge of $w_0$. Here we
+look at the situation where $w_0$ is known, but the learning rate $\eta$ is
+unknown. We also look at the most challenging case, when both $w_0$ and $\eta$
+are unknown at the start of teaching.
 
@@
 \cite{perceptron} used two metrics when analyzing their teaching strategies. The first was the exact 
-teaching dimension. The exact teaching dimension is the length of the shortest training sequence that 
-teaches a learner the desired concept.
+teaching dimension: the length of the shortest training sequence that teaches a learner the desired concept.
 
@@
 resultant weight vector after training on a sequence in $\mathbb{S}$, where $w_0$ is the initial weight 
-vector, and $\eta$ is the learning rate.
-Then if the teacher which to teach a concept $w^*$, then since $w^*$ describes a linear decision boundary then for any $c > 0$, $cw^*$ is parameterizes the same concept as $w^*$
-so the exact teaching dimension is 
+vector, and $\eta$ is the learning rate. Then if the teacher which to teach a
+concept $w^*$, since $w^*$ describes a linear decision boundary for any $c > 0$,
+$cw^*$ is parameterizes the same concept as $w^*$. So the exact teaching dimension is 
 $$
@@
 \subsection{$TD_\epsilon$}
-\cite{perceptron} also defined an approximate teaching dimension for cases where the exact teaching dimension was infinite but one could approximately teach a concept within $\epsilon$ distance.
-For perceptrons, the distance metric used was simply the 1 minus the cosine angle between $w^*$
-and $\learn(S)$
+\cite{perceptron} also defined an approximate teaching dimension for cases where
+the exact teaching dimension was infinite, but one could approximately teach a concept within $\epsilon$ distance.
+For perceptrons, the distance metric used was simply the 1 minus the cosine angle between $w^*$ and $\learn(S)$
 $$
@@
 
-Then let $\mathbb{T}_\epsilon$ be the set of $\epsilon-\text{approximate}$ teaching strategies for a decision boundary $w^*$. Then
+Then let $\mathbb{T}_\epsilon$ be the set of $\epsilon$-approximate teaching strategies for a decision boundary $w^*$. Then
 $$
@@
 
-\cite{perceptron} showed that when $w_0$ was unknown but $\eta$ was known $TD_\epsilon(w^*, \learn) = 3$
+\cite{perceptron} showed that when $w_0$ was unknown but $\eta$ was known, $TD_\epsilon(w^*, \learn) = 3$
 
@@
 \subsection{Using Unlabeled Examples}
-Before the teaching dimension was only analyzed with labeled examples.
+Before, the teaching dimension was only analyzed with labeled examples.
 Here we relax this constraint and allow unlabeled examples to be used in the teaching sequence.
@@
 \\
-\\
 \textit{Proof.}
@@
 \section{Teaching Dimension for unknown $\eta$ and $w_0$}
-Here we show a strategy where we know neither the learning rate or the initial weight vector of our perceptron learner.
-With prior knowledge of some reasonable bound on the magnitude of $w_0$ and $\eta$, we show a strategy that gives an upper bound on the approximate teaching dimension in this scenario.
+Here we present an algorithm that teaches the desired concept to the Perceptron learner when we know neither the learning rate, nor the initial weight vector of
+our perceptron learner, in ? steps.
 
+\subsection{$\epsilon$-Bounding the angle of $w_0$}
+Our algorithm will only consider the decision boundary and the weight vector of
+the Perceptron in two dimensions. In other words, we are considering the plane
+defined by
+\[
+  \begin{bmatrix}
+    a \\
+    b \\
+    0 \\
+    $\vdots$ \\
+    0
+  \end{bmatrix}
+  \textnormal{where}
+  \ a, b \in \textbb{R}
+\]
+\\
+\\
+In order to proceed, we must define an operation that creates an
+$\epsilon$-Bound around the angle of $w_o$ in the plane. It works by iteratively
+partitioning the plane with unlabeled examples. For convenience, let $(a,b)$
+denote a point in said plane. Let $ang(x,y)$ denote the angle between $x$ and
+$y$.
+
+\algnewcommand\algorithmicswitch{\textbf{switch}}
+\algnewcommand\algorithmiccase{\textbf{case}}
+
+\begin{algorithm}
+\caption{Bounding the angle of $w_0$}
+\begin{algorithmic}[1]
+	\REQUIRE $\epsilon$
+
+  \SWITCH{$sign(\langle w_0 , (0,1) \rangle)$, $sign(\langle w_0 , (1,0) \rangle)$}
+  \CASE
+
+  \ENDCASE
+  \ENDSWITCH
+  \IF{$\alpha \leftarrow (1,0)$}  \ENDIF
+
+	\STATE Select $(x_1 , y_1)$ s.t. $sign(\langle w^* , x_1 \rangle) = y_1 = -1 = 
+	-sign(\langle w_0 , x_1 \rangle )$
+	\STATE Give $(x_1, y_1)$ to the perceptron and allow to update.
+	\STATE $\alpha \leftarrow \eta_{\min}$
+	\STATE $\beta \leftarrow \eta_{\max}$
+
+	\WHILE{$\beta - \alpha > \epsilon$}
+		\STATE Select $ x_2$ s.t. $\langle w_0 , x_2 \rangle \neq 0, \langle x_1 , x_2 \rangle \neq 0$ and $\langle w_0, x_2 \rangle - \frac{\beta - \alpha}{2}\langle x_1, x_2 \rangle = 0$
+		\STATE Let the perceptron predict $\hat{y}$ for $x_2$
+		\IF{$\hat{y} = 1$}
+			\STATE $ \beta \leftarrow \frac{\beta - \alpha}{2}$ 		
+		\ELSE
+			\STATE $ \alpha \leftarrow \frac{\beta - \alpha}{2}$ 
+		\ENDIF	
+	\ENDWHILE   
+	\RETURN $(\alpha , \beta)$
+\end{algorithmic}
+\end{algorithm} 
+\textbf{textbf}
+
+\subsection{$\epsilon$-Bounding $\eta$}
+
+Assume $\exists b, \eta_{min}, \eta_{max} \in \mathbb{R}$ such that $\lVert w_0
+\rVert \leq b < \infty$ and $0 < \eta_{\min} \leq \eta \leq \eta_{\max} <
+\infty$.
+
+Now that we have a bound around $\eta$, we get to the main result.
+\\
+\\
 \textbf{Theorem 4.} 
@@
 }
-\\
 \\
@@
 \\
-\\
 \textbf{Theorem 5.} \textit{
@@
 
-\section*{References}
-
 \small

### 2017-05-04 paper_final.tex

@@
 \section{Introduction}
+====
+Mine
+
 In the real world, there are often scenarios where a teacher wishes to
@@
 completeness. The learning algorithm for the online perceptron is seen below.
+
+====
+Yours
+
+There may be a scenario where one entity, or the \textit{teacher},  has a desired target concept and a learner in which the teacher wants to embed that concept.
+In this scenario the teacher can only interact with the learner by constructing and then giving the learner a set of training examples.
+This constructive task is known as optimal teaching \cite{machine_teaching} \cite{teaching_dimension}.
+It has applications in education and security \cite{security}\cite{education} \cite{poisoning}.
+\cite{perceptron}\cite{td_linear} looked for the first time at online teaching in an online environment, with an online perceptron.
+In this paper we look at optimal teaching of the same perceptron, but now we give the teacher the ability to use unlabeled examples.
+Unlabeled examples allow the teacher to probe to discover more about the learners current state while not changing the learner.
+We show that this new added ability allows the teacher to teach an online perceptron in a scenario, that before may have been difficult.
+
+The specific perceptron we are teaching is the  online perceptron \cite{perceptron_algo}. The algorithm is designed for a binary classification. It can learn any linear decision boundary,
+with mapping $x \to sign(\langle w, x \rangle)$ where $x \in \mathbb{R}^d$ comes from the input space and $w \in \mathbb{R}^d$ parameterizes the perceptron.
+Here , as in \cite{perceptron}, $sign(0) = -1$ for completeness.
+The learning algorithm for the online perceptron is seen below.
+
+====
 

### 2017-05-04 paper_final.tex
Fixed merging and removed red comments

--- 2017-05-04 paper_final.tex
@@
 produces the desired concept in the learner is known as optimal teaching
-\cite{machine_teaching} \cite{teaching_dimension}. \cite{perceptron} looked for
+\cite{machine_teaching} \cite{teaching_dimension}\cite{td_linear}. It has applications in education and security \cite{security}\cite{education} \cite{poisoning}. \cite{perceptron} looked for
 the first time at optimal teaching in an online environment by proving the
@@
 Assume $w_0 \neq cw^*$ for arbitrary $c > 0$, then there exists an $(x_1, y_1)$ such that $\text{sign}(\langle w^*,x_1 \rangle) = y_1 = -1$ and $\text{sign}(\langle w_0,x_1 \rangle) = -y_1$.
-\color{red}
-I don't think that its hard to show this is true. But I won't prove for now
-\color{black}
 
@@
 $$
-\color{red}
-There should always be at least one solution to this. Again I won't prove for now.
-\color{black}
+There will always an $x_2$ with this property.
 
@@
 defined by
-\[
-  \begin{bmatrix}
-    a \\
-    b \\
-    0 \\
-    $\vdots$ \\
-    0
-  \end{bmatrix}
-  \textnormal{where}
-  \ a, b \in \textbb{R}
-\]
-\\
-\\
+
 In order to proceed, we must define an operation that creates an
@@
 $y$.
-
-\algnewcommand\algorithmicswitch{\textbf{switch}}
-\algnewcommand\algorithmiccase{\textbf{case}}
-
-\begin{algorithm}
-\caption{Bounding the angle of $w_0$}
-\begin{algorithmic}[1]
-	\REQUIRE $\epsilon$
-
-  \SWITCH{$sign(\langle w_0 , (0,1) \rangle)$, $sign(\langle w_0 , (1,0) \rangle)$}
-  \CASE
-
-  \ENDCASE
-  \ENDSWITCH
-  \IF{$\alpha \leftarrow (1,0)$}  \ENDIF
-
-	\STATE Select $(x_1 , y_1)$ s.t. $sign(\langle w^* , x_1 \rangle) = y_1 = -1 = 
-	-sign(\langle w_0 , x_1 \rangle )$
-	\STATE Give $(x_1, y_1)$ to the perceptron and allow to update.
-	\STATE $\alpha \leftarrow \eta_{\min}$
-	\STATE $\beta \leftarrow \eta_{\max}$
-
-	\WHILE{$\beta - \alpha > \epsilon$}
-		\STATE Select $ x_2$ s.t. $\langle w_0 , x_2 \rangle \neq 0, \langle x_1 , x_2 \rangle \neq 0$ and $\langle w_0, x_2 \rangle - \frac{\beta - \alpha}{2}\langle x_1, x_2 \rangle = 0$
-		\STATE Let the perceptron predict $\hat{y}$ for $x_2$
-		\IF{$\hat{y} = 1$}
-			\STATE $ \beta \leftarrow \frac{\beta - \alpha}{2}$ 		
-		\ELSE
-			\STATE $ \alpha \leftarrow \frac{\beta - \alpha}{2}$ 
-		\ENDIF	
-	\ENDWHILE   
-	\RETURN $(\alpha , \beta)$
-\end{algorithmic}
-\end{algorithm} 
-\textbf{textbf}
 

### 2017-05-05 paper_final.tex
Checked and cleaned up all proofs

@@
   there is even less knowledge of the Perceptron's initial state, but the
-  teacher is given extra powers to compensate. We present an efficient algorithm
-  to force the learner into a desired state with no knowledge of the learner's
-  initial state. We also analyze a setting in which a teacher has the ability to
+  teacher is given extra powers to compensate.
+We present two teaching strategies that take advantage of unlabeled examples to teach a perceptron.
+We also analyze a another strategy in which a teacher has the ability to
   lie.
@@
 \cite{machine_teaching} \cite{teaching_dimension}\cite{td_linear}. It has applications in education and security \cite{security}\cite{education} \cite{poisoning}. \cite{perceptron} looked for
-the first time at optimal teaching in an online environment by proving the
-optimal teaching dimension in an online Perceptron. In this paper we look at the
+the first time at optimal teaching in an online environment by finding the teaching dimension of an online perceptron. In this paper we look at the
 optimal teaching of the same perceptron, but with a teacher that also possess
@@
 learner's state. This is a reasonable power for any real-world teacher to
-posses. We show that this added ability allows the teacher to teach an
+posses. We show that this added ability, with the exclusion of some worst case scenarios, allows the teacher to teach an
 online perceptron in a zero-knowledge scenario that otherwise would have been
@@
 
-\section{Teaching Dimension}
-\cite{perceptron} used two metrics when analyzing their teaching strategies. The first was the exact 
-teaching dimension: the length of the shortest training sequence that teaches a learner the desired concept.
-
-\subsection{$TD_{exact}$}
-
-Formally, let $\mathbb{S}$ be the space of finite training 
-sequences. Then let $\mathcal{A}_{w_0}^{\eta} : \mathbb{S} \to \mathbb{R}^d$ be a function the gives the 
-resultant weight vector after training on a sequence in $\mathbb{S}$, where $w_0$ is the initial weight 
-vector, and $\eta$ is the learning rate. Then if the teacher which to teach a
-concept $w^*$, since $w^*$ describes a linear decision boundary for any $c > 0$,
-$cw^*$ is parameterizes the same concept as $w^*$. So the exact teaching dimension is 
-$$
-TD_{exact}(w^*, \mathcal{A}_{w_0}^\eta) = \min\{ \lvert S \rvert : 
-\mathcal{A}_{w_0}^\eta(S) = cw^* \text{ for some } c >0 \}
-$$
-
-\cite{perceptron} showed that when $\eta$ and $w_0$ where known, $TD_{exact}(w^*, \mathcal{A}_{w_0}^\eta) = 1$
-
-\subsection{$TD_\epsilon$}
-\cite{perceptron} also defined an approximate teaching dimension for cases where
+\section{Approximate Teaching Dimension}
+\cite{perceptron}  defined an approximate teaching dimension for cases where
 the exact teaching dimension was infinite, but one could approximately teach a concept within $\epsilon$ distance.
@@
 $$
-
+where $\learn$ is the learning algorithm and $S$ is the training sequence. 
 \cite{perceptron} showed that when $w_0$ was unknown but $\eta$ was known, $TD_\epsilon(w^*, \learn) = 3$
@@
 \textbf{Theorem 2.}
-\textit{ If $w_0$ is known , $w_0 \leq b < \infty$ and $ 0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ 
+\textit{ If $w_0$ is known , $\lVert w_0 \rVert \leq b < \infty$ and $ 0 < \eta_{\min} \leq \eta \leq \eta_{\max} < \infty$ 
 then $\mathbb{T}_{\epsilon}(w^*, \learn)  \leq 2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$
@@
 
-Use this $(x_1, y_1)$ in \textbf{Algorithm 2} to get a bound on $\eta$ such that $\eta \in [\alpha , \beta]$ and $\beta - \alpha <= 2\epsilon \eta_{\max}$
+Use this $(x_1, y_1)$ in \textbf{Algorithm 2} to get a bound on $\eta$ such that $\eta \in [\alpha , \beta]$ and $\beta - \alpha \leq 2\epsilon \eta_{\max}$
 
@@
 y_2 \langle w_1, x_2 \rangle  = \bigg\langle \frac{2 b}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0 - \eta x_1 \bigg\rangle
-$$
-$$
 = \bigg\langle \frac{2 b}{\epsilon (\beta + \alpha) /2} w^* + x_1 , w_0  \bigg\rangle - \eta \lVert x_1 \rVert^2
@@
 \leq \bigg( \frac{2 b}{\epsilon (\beta + \alpha) /2} \lVert w^* \rVert + \lVert x_1 \rVert \bigg ) b - \eta \lVert x_1 \rVert^2
-$$
-$$
 \leq \frac{4 b ^2}{\epsilon \eta_{\min}} - \eta \frac{4 b^2}{\epsilon^2 \eta_{\min}^2}
-$$
-$$
 \leq \frac{4 b^2}{\epsilon \eta_{\min}}  -  \frac{4 b^2}{\epsilon^2 \eta_{\min}}
@@
 \geq \frac{\frac{\eta 2  b}{\epsilon (\beta + \alpha)/2} - b}{b +\frac{\eta 2  \lVert w_0 \rVert}{\epsilon (\beta + \alpha)/2} }
-$$
-$$
 = 1 - \frac{2 b}{b +\frac{\eta 2  b}{\epsilon (\beta + \alpha)/2} }
-$$
-$$
 = 1 - \frac{2b}{b \epsilon + \frac{\eta 2  b}{(\beta + \alpha)/2} } \epsilon
@@
 \geq  1 - \frac{2b}{b \epsilon + \frac{\eta 2  b}{\eta_{\max} - (\beta - \alpha) / 2} } \epsilon
-$$
-$$
 \geq  1 - \frac{2b}{b \epsilon + \frac{\eta 2  b}{\eta_{\max} (1-\epsilon)} } \epsilon
-$$
-$$
 \geq 1 - \frac{2b}{b \epsilon + \frac{ 2  b}{(1-\epsilon)} } \epsilon
@@
 Therefore 
-$\mathbb{T}_\epsilon \leq  2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$
+$\mathbb{T}_\epsilon(w^* ,\learn) \leq  2 + \lceil \log_2 \frac{\eta_{\max} - \eta_{\min}}{2\epsilon\eta_{\max}}  \rceil$
+
+\subsection{Tightness of Bound}
+We believe the bound in \textbf{Theorem 2} is tight.
+There are examples for which a single labeled example will not be able to guarantee our $\epsilon$ upper bound without a better bound on the learning rate.
+And we believe \textbf{Algorithm 2} is optimal for bounding the learning rate.
+Further work will need to be done to prove the tightness of \textbf{Theorem 2}.
 
@@
 Here we present an algorithm that teaches the desired concept to the Perceptron learner when we know neither the learning rate, nor the initial weight vector of
-our perceptron learner, in ? steps.
+our perceptron learner.
 
@@
 $
-\mathbb{T}_\epsilon(w^* , \learn) \leq 3 + ?
+\mathbb{T}_\epsilon(w^* , \learn) \leq 3 + T_{\text{bound}}(2\epsilon \eta_{\max})
 $
+where $T_{\text{bound}}(2\epsilon \eta_{\max})$ is the worst case number of examples needed to bound $\eta \in [\alpha , \beta]$ s.t. $\beta - \alpha \leq 2\epsilon \eta_{\max}$
 }
@@
 \textit{Proof.}
-First using \textbf{Algorithm 3} bound $\eta$ such that $ \alpha \leq \eta \leq \beta$ and $\beta - \alpha \leq 2\epsilon \eta_{\max}$
+First bound $\eta$ such that $ \alpha \leq \eta \leq \beta$ and $\beta - \alpha \leq 2\epsilon \eta_{\max}$
 
-Then WLOG assume $\lVert w^8 \rVert = 1$. Then pick an $x_1$ such that 
+Then WLOG assume $\lVert w^* \rVert = 1$. Then pick an $x_1$ such that 
 $\lVert x_1 \rVert = \frac{2b}{\epsilon (\beta + \alpha)/2}$ and $\langle w^*, x_1 \rangle = 0$.
@@
 So first give $(x_1, y_1)$ to the perceptron.
-\underline{Case 1}: If $(x_1, y_1)$ then $w_1 = w_0 - \eta x_1$. 
+
+\underline{Case 1}: If $(x_1, y_1)$ causes an update then $w_1 = w_0 - \eta x_1$. 
 Then select at the second iteration an $x_2 = \frac{2b}{\epsilon (\beta + \alpha)/2}$. Using the same logic from theorem 2, we can see that this will give us our desired $\epsilon$ approximate $w_2$.
@@
 $$
-\mathbb{T}_\epsilon(w^*, \learn) \leq 3 + ?
+\mathbb{T}_\epsilon(w^*, \learn) \leq 3 + T_{\text{bound}}(2\epsilon \eta_{\max})
 $$
@@
 
-\textbf{Case 1:} The perceptron incorrectly predicts $y = 1$ for $x_1$.
+\underline{Case 1:} The perceptron incorrectly predicts $y = 1$ for $x_1$.
 
@@
 Then 
-$$y_2 \langle w_1, 2x_1 \rangle
+$$y_2 \langle w_1, x_2 \rangle
+ = \langle w_0, 2x_1 \rangle - 2\frac{(\eta b(2-\epsilon))^2}{(\eta_{\min}\epsilon)^2}
 $$
 $$
- = \langle w_0, 2x_1 \rangle - 2\frac{(\eta b(2-\epsilon))^2}{(\eta_{\min}\epsilon)^2}
  \leq 2b\frac{\eta b(2-\epsilon)}{\eta_{\min}\epsilon}
@@
 
-\textbf{Case 2:} $(x_1, y_1)$ does not cause an update.
+\underline{Case 2:} $(x_1, y_1)$ does not cause an update.
 
@@
 
+\section{Conclusion}
+
 \small

### 2017-05-05 paper_final.tex
Added discussion section

@@
 
-\section{Conclusion}
+\section{Discussion}
+Here we've shown some interesting bounds.
+Though not all tight they still highlight some of the security risks of perceptrons.
+If a perceptron were used on a web-server, any of these algorithms would be efficient enough to hack the perceptron to believe whatever decision boundary we like.
+As well these findings highlight the power of lying in Machine Teaching.
+With the ability to lie, teaching a perceptron becomes trivial.
+One further venture would be to look into other learning algorithms that could be taught efficiently with lying.
 

### 2017-05-05 paper_final.tex
final Bullcrap

--- 2017-05-04 paper_final.tex
@@
 \usepackage{bbm}
+\usepackage{mathtools}
+\DeclarePairedDelimiter{\ceil}{\lceil}{\rceil}
 
@@
 produces the desired concept in the learner is known as optimal teaching
-\cite{machine_teaching} \cite{teaching_dimension}\cite{td_linear}. It has applications in education and security \cite{security}\cite{education} \cite{poisoning}. \cite{perceptron} looked for
+\cite{machine_teaching} \cite{teaching_dimension}. \cite{perceptron} looked for
 the first time at optimal teaching in an online environment by proving the
@@
 Assume $w_0 \neq cw^*$ for arbitrary $c > 0$, then there exists an $(x_1, y_1)$ such that $\text{sign}(\langle w^*,x_1 \rangle) = y_1 = -1$ and $\text{sign}(\langle w_0,x_1 \rangle) = -y_1$.
+\color{red}
+I don't think that its hard to show this is true. But I won't prove for now
+\color{black}
 
@@
 $$
-There will always an $x_2$ with this property.
+\color{red}
+There should always be at least one solution to this. Again I won't prove for now.
+\color{black}
 
@@
 
-\section{Teaching Dimension for unknown $\eta$ and $w_0$}
-Here we present an algorithm that teaches the desired concept to the Perceptron learner when we know neither the learning rate, nor the initial weight vector of
-our perceptron learner, in ? steps.
+\section{Discussions of the teaching dimension for unknown $\eta$ and $w_0$}
+
+We present an algorithm that teaches the desired concept to the Perceptron
+learner when we know neither the learning rate, nor the initial weight vector of
+our perceptron learner. The algorithm works well in general, but there is a very
+unlikely case that will cause the number of unsupervised queries to diverge to
+infinity. We also discuss a potential problem in the definition of the teaching
+dimension and prove an upper bound on the teaching dimension in this setting
+given an optimal algorithm for bounding $\eta$.
 
@@
 the Perceptron in two dimensions. In other words, we are considering the plane
-defined by
-
+defined by,
+\[
+  \begin{bmatrix}
+    a & b & 0 & \cdots & 0
+  \end{bmatrix} ^ \top
+  \textnormal{where}
+  \ a, b \in \mathbb{R}
+\]
+The decision boundary of the Perceptron passes through the origin, so it will
+also pass through the origin of this plane and create a linear decision
+boundary.
+\\
 In order to proceed, we must define an operation that creates an
@@
 denote a point in said plane. Let $ang(x,y)$ denote the angle between $x$ and
-$y$.
+$y$. Let $mid(x, y)$ be the midpoint between $x$ and $y$ on the unit circle
+($x$ and $y$ have the same magnitude). Let $test(\alpha)$ be an unsupervised
+check of $\alpha$.
+
+\begin{algorithm}
+\caption{Bounding the angle of $w_0$}
+\begin{algorithmic}[1]
+	\REQUIRE $\epsilon$
+  \STATE Compute $test((0,1))$, $test((1,0))$, and $test((0,-1))$
+
+  \COMMENT{One of these will be different from the others, or $w_0 \in
+  \{(1,0), (-1,0)\}$, in which case we're done.}
+  \STATE $\alpha \leftarrow $ the different one, $\beta \leftarrow $ the one
+  next to $\alpha$.
+  \FOR{$i \leftarrow \frac{1}{4}$; $i > \epsilon$; $ i \leftarrow \frac{i}{2}$}
+  \IF{$test(mid(\alpha,\beta)) \ != test(\alpha)$}
+  \STATE $\beta \leftarrow mid(\alpha, \beta)$
+  \ELSE
+  \STATE $\alpha \leftarrow mid(\alpha, \beta)$
+  \ENDIF
+  \ENDFOR
+  \RETURN $\alpha$, $\beta$
+
+\end{algorithmic}
+\end{algorithm}
+
+This gets us a bound around the angle of $w_0$ in time $\ceil{log(\frac{1}{\epsilon})} +
+1$.
 
@@
 
-Assume $\exists b, \eta_{min}, \eta_{max} \in \mathbb{R}$ such that $\lVert w_0
-\rVert \leq b < \infty$ and $0 < \eta_{\min} \leq \eta \leq \eta_{\max} <
-\infty$.
+Now that we know that we can move and bound the angle of $w_0$, we can bound
+$\eta$. The algorithm works by giving the perceptron a ``large enough'' update,
+two times. Because the update is vector addition, the size of the update is a
+linear combination of $\eta$ and $\lVert w_0 \rVert$. With two equations and two
+unknowns, we can derive both $\eta$ and $\lVert w_0 \rVert$. Using basic trig,
+we get,
 
-Now that we have a bound around $\eta$, we get to the main result.
+\[
+  \begin{cases}
+    \lVert w_0 \rVert * \tan(\theta_1) + \eta * \lVert x \rVert (\tan(\theta_1)  
+    \cos{\phi} - \sin{\phi}) = 0 \\
+
+    \lVert w_0 \rVert * \tan(\theta_2) + \eta * 2 \lVert x \rVert (\tan(\theta_2)
+    \cos{\phi} - \sin{\phi}) = 0 \\
+  \end{cases}
+\]
+\textit{where $\theta_1, \theta_2$ are the angles of the updated $w$'s with
+  $w_0$, $\phi$ is the angle of the training case with $w_0$, and $x$ is our
+  training example.}
+
+\begin{algorithm}
+\caption{Bounding $\eta$}
+\begin{algorithmic}[1]
+	\REQUIRE $\epsilon'$: desired bound around the concept $w^*$
+  \STATE $\alpha_1, \beta,_1 \leftarrow$ bounds around $w_0$ such that $w^*$ is not
+  inside it
+
+  \COMMENT{If we detect that $ang(\alpha_1, \beta_1) < \epsilon'$, we can quit the
+    whole teaching procedure because the learner knows the concept.}
+  \STATE $x' \leftarrow $ the most perpendicular vector to $mid(\alpha_1, \beta_1)$
+  that causes an update
+  \STATE $v \leftarrow$ constant ``large enough'' to make the perceptron update
+  \STATE $teach(x' * v)$
+  \STATE $\alpha_2, \beta_2 \leftarrow$ ``small enough'' bound around $w$
+  \STATE $teach(x' * v)$
+  \STATE $\alpha_3, \beta_3 \leftarrow$ ``small enough'' bound around $w$
+  \STATE Solve the linear equation defined above 8 times using every combination of
+  $\alpha$ and $\beta$. The $\epsilon$-Bound is the worst case of these.
+\end{algorithmic}
+\end{algorithm}
+
+The problem with this algorithm appear in step 3; it is possible to come up with
+concrete definitions for Steps 2, 5, 7. We can construct a case where
+$\alpha_1$ and $\beta_1$ are as close as possible, without being $ < \epsilon'$,
+and $w^*$ is arbitrarily close to $\alpha$. This situation can require
+arbitrarily tight bounds on the angle of $w_0$, requiring arbitrarily many
+unsupervised queries.
+\subsection{Discussions of the Definition of Teaching Dimension}
+Given that the algorithm works well in general, but diverges in certain pathological
+cases, we suggest that an extension of the concept of the teaching dimension
+could be useful for dealing with Machine Teaching in more complex settings.
+Instead of Minmaxing the number of examples, we propose that the expected value
+of a teaching algorithm is a more interesting metric. There is a parallel to
+statistical learning theory: instead of using the ``minimax
+rule'' to minimize the Risk, it is better to minimize the expected Risk.
+
+\subsection{Main Result}
 \\
@@
 \textit{Proof.}
-First using \textbf{Algorithm 3} bound $\eta$ such that $ \alpha \leq \eta \leq \beta$ and $\beta - \alpha \leq 2\epsilon \eta_{\max}$
+First using \textbf{Algorithm 4} bound $\eta$ such that $ \alpha \leq \eta \leq \beta$ and $\beta - \alpha \leq 2\epsilon \eta_{\max}$
 
@@
 
-\subsection{Ability to Lie}
+\section{Ability to Lie}
 Allowing the teacher to lie, or give $(x,y)$ that disagree with $w^*$, make teaching the learner very easy. In fact in this scenario, the approximate teaching dimension is $2$.

### 2017-05-05 paper_final.tex

--- 2017-05-05 paper_final.tex
@@
 
-\section{Teaching Dimension for unknown $\eta$ and $w_0$}
-Here we present an algorithm that teaches the desired concept to the Perceptron learner when we know neither the learning rate, nor the initial weight vector of
-our perceptron learner.
+\section{Discussions of the teaching dimension for unknown $\eta$ and $w_0$}
+
+We present an algorithm that teaches the desired concept to the Perceptron
+learner when we know neither the learning rate, nor the initial weight vector of
+our perceptron learner. The algorithm works well in general, but there is a very
+unlikely case that will cause the number of unsupervised queries to diverge to
+infinity. We also discuss a potential problem in the definition of the teaching
+dimension and prove an upper bound on the teaching dimension in this setting
+given an optimal algorithm for bounding $\eta$.
 
@@
 the Perceptron in two dimensions. In other words, we are considering the plane
-defined by
+
+defined by,
+\[
+  \begin{bmatrix}
+    a & b & 0 & \cdots & 0
+  \end{bmatrix} ^ \top
+  \textnormal{where}
+  \ a, b \in \mathbb{R}
+\]
+The decision boundary of the Perceptron passes through the origin, so it will
+also pass through the origin of this plane and create a linear decision
+boundary.
+\\
 
@@
 
-Assume $\exists b, \eta_{min}, \eta_{max} \in \mathbb{R}$ such that $\lVert w_0
-\rVert \leq b < \infty$ and $0 < \eta_{\min} \leq \eta \leq \eta_{\max} <
-\infty$.
+Now that we know that we can move and bound the angle of $w_0$, we can bound
+$\eta$. The algorithm works by giving the perceptron a ``large enough'' update,
+two times. Because the update is vector addition, the size of the update is a
+linear combination of $\eta$ and $\lVert w_0 \rVert$. With two equations and two
+unknowns, we can derive both $\eta$ and $\lVert w_0 \rVert$. Using basic trig,
+we get,
 
-Now that we have a bound around $\eta$, we get to the main result.
-\\
-\\
+\[
+  \begin{cases}
+    \lVert w_0 \rVert * \tan(\theta_1) + \eta * \lVert x \rVert (\tan(\theta_1)  
+    \cos{\phi} - \sin{\phi}) = 0 \\
+
+    \lVert w_0 \rVert * \tan(\theta_2) + \eta * 2 \lVert x \rVert (\tan(\theta_2)
+    \cos{\phi} - \sin{\phi}) = 0 \\
+  \end{cases}
+\]
+\textit{where $\theta_1, \theta_2$ are the angles of the updated $w$'s with
+  $w_0$, $\phi$ is the angle of the training case with $w_0$, and $x$ is our
+  training example.}
+
+\begin{algorithm}
+\caption{Bounding $\eta$}
+\begin{algorithmic}[1]
+	\REQUIRE $\epsilon'$: desired bound around the concept $w^*$
+  \STATE $\alpha_1, \beta,_1 \leftarrow$ bounds around $w_0$ such that $w^*$ is not
+  inside it
+
+  \COMMENT{If we detect that $ang(\alpha_1, \beta_1) < \epsilon'$, we can quit the
+    whole teaching procedure because the learner knows the concept.}
+  \STATE $x' \leftarrow $ the most perpendicular vector to $mid(\alpha_1, \beta_1)$
+  that causes an update
+  \STATE $v \leftarrow$ constant ``large enough'' to make the perceptron update
+  \STATE $teach(x' * v)$
+  \STATE $\alpha_2, \beta_2 \leftarrow$ ``small enough'' bound around $w$
+  \STATE $teach(x' * v)$
+  \STATE $\alpha_3, \beta_3 \leftarrow$ ``small enough'' bound around $w$
+  \STATE Solve the linear equation defined above 8 times using every combination of
+  $\alpha$ and $\beta$. The $\epsilon$-Bound is the worst case of these.
+\end{algorithmic}
+\end{algorithm}
+
+The problem with this algorithm appear in step 3; it is possible to come up with
+concrete definitions for Steps 2, 5, 7. We can construct a case where
+$\alpha_1$ and $\beta_1$ are as close as possible, without being $ < \epsilon'$,
+and $w^*$ is arbitrarily close to $\alpha$. This situation can require
+arbitrarily tight bounds on the angle of $w_0$, requiring arbitrarily many
+unsupervised queries.
+\subsection{Discussions of the Definition of Teaching Dimension}
+Given that the algorithm works well in general, but diverges in certain pathological
+cases, we suggest that an extension of the concept of the teaching dimension
+could be useful for dealing with Machine Teaching in more complex settings.
+Instead of Minmaxing the number of examples, we propose that the expected value
+of a teaching algorithm is a more interesting metric. There is a parallel to
+statistical learning theory: instead of using the ``minimax
+rule'' to minimize the Risk, it is better to minimize the expected Risk.
+
+\subsection{Main Result}
 \textbf{Theorem 4.} 
@@
 \textit{Proof.}
+
 First bound $\eta$ such that $ \alpha \leq \eta \leq \beta$ and $\beta - \alpha \leq 2\epsilon \eta_{\max}$

### 2017-05-05 paper_final.tex
Final Content check

@@
 unlikely case that will cause the number of unsupervised queries to diverge to
-infinity. We also discuss a potential problem in the definition of the teaching
+infinity. We also discuss a potential alteration to the definition of the teaching
 dimension and prove an upper bound on the teaching dimension in this setting
@@
 Our algorithm will only consider the decision boundary and the weight vector of
-the Perceptron in two dimensions. In other words, we are considering the plane
-
-defined by,
+the Perceptron in two dimensions. In other words, we are considering the plane defined by,
 \[
@@
 boundary.
-\\
 
@@
 \section{Discussion}
-Here we've shown some interesting bounds.
-Though not all tight they still highlight some of the security risks of perceptrons.
-If a perceptron were used on a web-server, any of these algorithms would be efficient enough to hack the perceptron to believe whatever decision boundary we like.
-As well these findings highlight the power of lying in Machine Teaching.
-With the ability to lie, teaching a perceptron becomes trivial.
-One further venture would be to look into other learning algorithms that could be taught efficiently with lying.
+Here we've shown some interesting bounds. Though they are not all tight, they
+still highlight some of the security risks of perceptrons. If a perceptron were
+used on a web-server, any of these algorithms would be efficient enough to hack
+the perceptron to believe whatever decision boundary we like. These findings
+also highlight the power of lying in Machine Teaching. With the ability to lie,
+teaching a perceptron becomes trivial. One extension would be to look into other learning algorithms that could be taught efficiently with lying.
 
